### 2023-08-02 draft/v1.tex
new draft setup

\documentclass{article}

\begin{document}

Something
\end{document}

### 2023-08-04 draft/assets/main.tex
added a template

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\linenumbers

\title{Data Descriptor Title (110 character maximum, inc. spaces)}

\author[1,$\dag$]{Alice Author}
\author[2,$\dag$]{Bob Author}
\author[1,2]{Christine Author}
\author[2,*]{Derek Author}
\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}

\affil[*]{corresponding author(s): Derek Author (corresponding.author@email.example)}

\affil[$\dag$]{these authors contributed equally to this work}

\begin{abstract}
This is a manuscript template for Data Descriptor submissions to \emph{Scientific Data} (\href{http://www.nature.com/scientificdata}{http://www.nature.com/scientificdata}). The abstract must be no longer than 170 words, and should succinctly describe the study, the assay(s) performed, the resulting data, and the reuse potential, but should not make any claims regarding new scientific findings. No references are allowed in this section. 
\end{abstract}
\begin{document}

\flushbottom
\maketitle
%  Click the title above to edit the author information and abstract

\thispagestyle{empty}

\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists or tables should be included. Structure of the main text is provided below.

\section*{Background \& Summary}

(700 words maximum) An overview of the study design, the assay(s) performed, and the created data, including any background information needed to put this study in the context of previous work and the literature. The section should also briefly outline the broader goals that motivated the creation of this dataset and the potential reuse value. We also encourage authors to include a figure that provides a schematic overview of the study and assay(s) design. The Background \& Summary should not include subheadings. This section and the other main body sections of the manuscript should include citations to the literature as needed.

\section*{Methods}

The Methods should include detailed text describing any steps or procedures used in producing the data, including full descriptions of the experimental design, data acquisition assays, and any computational processing (e.g. normalization, image feature extraction). See the detailed section in our submission guidelines for advice on writing a transparent and reproducible methods section. Related methods should be grouped under corresponding subheadings where possible, and methods should be described in enough detail to allow other researchers to interpret and repeat, if required, the full study. Specific data outputs should be explicitly referenced via data citation (see Data Records and Citing Data, below).

Authors should cite previous descriptions of the methods under use, but ideally the method descriptions should be complete enough for others to understand and reproduce the methods and processing steps without referring to associated publications. There is no limit to the length of the Methods section. Subheadings should not be numbered.

\subsection*{Subsection}

Example text under a subsection. Bulleted lists may be used where appropriate, e.g.

\begin{itemize}
\item First item
\item Second item
\end{itemize}

\subsubsection*{Third-level section}

Topical subheadings are allowed.

\section*{Data Records}

The Data Records section should be used to explain each data record associated with this work, including the repository where this information is stored, and to provide an overview of the data files and their formats. Each external data record should be cited numerically in the text of this section, for example \cite{Hao:gidmaps:2014}, and included in the main reference list as described below. A data citation should also be placed in the subsection of the Methods containing the data-collection or analytical procedure(s) used to derive the corresponding record. Providing a direct link to the dataset may also be helpful to readers (\hyperlink{https://doi.org/10.6084/m9.figshare.853801}{https://doi.org/10.6084/m9.figshare.853801}).

Tables should be used to support the data records, and should clearly indicate the samples and subjects (study inputs), their provenance, and the experimental manipulations performed on each (please see 'Tables' below). They should also specify the data output resulting from each data-collection or analytical step, should these form part of the archived record.

\section*{Technical Validation}

This section presents any experiments or analyses that are needed to support the technical quality of the dataset. This section may be supported by figures and tables, as needed. This is a required section; authors must present information justifying the reliability of their data.

\section*{Usage Notes}

The Usage Notes should contain brief instructions to assist other researchers with reuse of the data. This may include discussion of software packages that are suitable for analysing the assay data files, suggested downstream processing steps (e.g. normalization, etc.), or tips for integrating or comparing the data records with other datasets. Authors are encouraged to provide code, programs or data-processing workflows if they may help others understand or use the data. Please see our code availability policy for advice on supplying custom code alongside Data Descriptor manuscripts.

For studies involving privacy or safety controls on public access to the data, this section should describe in detail these controls, including how authors can apply to access the data, what criteria will be used to determine who may access the data, and any limitations on data use.

\section*{Code availability}

For all studies using custom code in the generation or processing of datasets, a statement must be included under the heading "Code availability", indicating whether and how the code can be accessed, including any restrictions to access. This section should also include information on the versions of any software used, if relevant, and any specific variables or parameters used to generate, test, or process the current dataset.

\bibliography{sample}

\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g. \cite{Kaufman2020, Figueredo:2009dg, Babichev2002, behringer2014manipulating}. For data citations of datasets uploaded to e.g. \emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file. For journal articles, DOIs should be included for works in press that do not yet have volume or page numbers. For other journal articles, DOIs should be included uniformly for all articles or not at all. We recommend that you encode all DOIs in your bibtex database as full URLs, e.g. https://doi.org/10.1007/s12110-009-9068-2.

\section*{Acknowledgements} (not compulsory)

Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.

\section*{Author contributions statement}

Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s), A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results. All authors reviewed the manuscript.

\section*{Competing interests} (mandatory statement)

The corresponding author is responsible for providing a \href{https://www.nature.com/sdata/policies/editorial-and-publishing-policies#competing}{competing interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

\section*{Figures \& Tables}

Figures, tables, and their legends, should be included at the end of the document. Figures and tables can be referenced in \LaTeX{} using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.

Authors are encouraged to provide one or more tables that provide basic information on the main ‘inputs’ to the study (e.g. samples, participants, or information sources) and the main data outputs of the study. Tables in the manuscript should generally not be used to present primary data (i.e. measurements). Tables containing primary data should be submitted to an appropriate data repository.

Tables may be provided within the \LaTeX{} document or as separate files (tab-delimited text or Excel files). Legends, where needed, should be included here. Generally, a Data Descriptor should have fewer than ten Tables, but more may be allowed when needed. Tables may be of any size, but only Tables which fit onto a single printed page will be included in the PDF version of the article (up to a maximum of three).

Due to typesetting constraints, tables that do not fit onto a single A4 page cannot be included in the PDF version of the article and will be made available in the online version only. Any such tables must be labelled in the text as ‘Online-only’ tables and numbered separately from the main table list e.g. ‘Table 1, Table 2, Online-only Table 1’ etc.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{stream}
\caption{Legend (350 words max). Example legend text.}
\label{fig:stream}
\end{figure}

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
Condition & n & p \\
\hline
A & 5 & 0.1 \\
\hline
B & 10 & 0.01 \\
\hline
\end{tabular}
\caption{\label{tab:example}Legend (350 words max). Example legend text.}
\end{table}

\end{document}

### 2023-08-04 draft/v1.tex
revised the introduction

@@
-\documentclass{article}
+\documentclass[fleqn,10pt]{wlscirep}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{lineno}
+\linenumbers
+
+\title{U.S. Laws and their Revision Histories}
+
+\author[$\dag$]{Brian Libgober}
+\affil[$\dag$]{Northwestern University, Department of Political Science and School of Law, Evanston, IL, 60202, USA. brian.libgober@northwestern.edu}
+
+\begin{abstract}
+Lists of US laws figure importantly in many research projects in political science, law, sociology, economics, and other disciplines.
+Yet despite their prominence and frequent use, there is no authoritative and complete dataset of all US laws.
+In part, this is because US laws have been enacted over hundreds of years, resulting in a complicated patchwork published in numerous and inconsistent formats.
+As a simplification, many scholars have relied upon more selective lists of \textit{major} legislative enactments, although the selection criteria for these narrower lists make their use questionable in many cases.
+Here, we describe our efforts to create a complete database of US laws and their revision histories by combining data from HEINOnline, Congress.gov, the Office of Revision Counsel, and other sources.
+Using these data, we can describe for the first time the network of US laws and calculate previously unknown quantities derived from the network data (e.g.
+how long does a law on average go without revision?).
+\end{abstract}
 
@@
 
-Something
+\flushbottom
+\maketitle
+%  Click the title above to edit the author information and abstract
+
+\thispagestyle{empty}
+
+\section*{Background \& Summary}
+
+(700 words maximum) An overview of the study design, the assay(s) performed, and the created data, including any background information needed to put this study in the context of previous work and the literature.
+The section should also briefly outline the broader goals that motivated the creation of this dataset and the potential reuse value.
+We also encourage authors to include a figure that provides a schematic overview of the study and assay(s) design.
+The Background \& Summary should not include subheadings.
+This section and the other main body sections of the manuscript should include citations to the literature as needed.
+
+\section*{Methods}
+
+The Methods should include detailed text describing any steps or procedures used in producing the data, including full descriptions of the experimental design, data acquisition assays, and any computational processing (e.g.
+normalization, image feature extraction).
+See the detailed section in our submission guidelines for advice on writing a transparent and reproducible methods section.
+Related methods should be grouped under corresponding subheadings where possible, and methods should be described in enough detail to allow other researchers to interpret and repeat, if required, the full study.
+Specific data outputs should be explicitly referenced via data citation (see Data Records and Citing Data, below).
+
+Authors should cite previous descriptions of the methods under use, but ideally the method descriptions should be complete enough for others to understand and reproduce the methods and processing steps without referring to associated publications.
+There is no limit to the length of the Methods section.
+Subheadings should not be numbered.
+
+\subsection*{Subsection}
+
+Example text under a subsection. Bulleted lists may be used where appropriate, e.g.
+
+\begin{itemize}
+\item First item
+\item Second item
+\end{itemize}
+
+\subsubsection*{Third-level section}
+
+Topical subheadings are allowed.
+
+\section*{Data Records}
+
+The Data Records section should be used to explain each data record associated with this work, including the repository where this information is stored, and to provide an overview of the data files and their formats.
+Each external data record should be cited numerically in the text of this section, for example \cite{Hao:gidmaps:2014}, and included in the main reference list as described below.
+A data citation should also be placed in the subsection of the Methods containing the data-collection or analytical procedure(s) used to derive the corresponding record.
+Providing a direct link to the dataset may also be helpful to readers (\hyperlink{https://doi.org/10.6084/m9.figshare.853801}{https://doi.org/10.6084/m9.figshare.853801}).
+
+Tables should be used to support the data records, and should clearly indicate the samples and subjects (study inputs), their provenance, and the experimental manipulations performed on each (please see 'Tables' below).
+They should also specify the data output resulting from each data-collection or analytical step, should these form part of the archived record.
+
+\section*{Technical Validation}
+
+This section presents any experiments or analyses that are needed to support the technical quality of the dataset.
+This section may be supported by figures and tables, as needed.
+This is a required section; authors must present information justifying the reliability of their data.
+
+\section*{Usage Notes}
+
+The Usage Notes should contain brief instructions to assist other researchers with reuse of the data.
+This may include discussion of software packages that are suitable for analysing the assay data files, suggested downstream processing steps (e.g.
+normalization, etc.), or tips for integrating or comparing the data records with other datasets.
+Authors are encouraged to provide code, programs or data-processing workflows if they may help others understand or use the data.
+Please see our code availability policy for advice on supplying custom code alongside Data Descriptor manuscripts.
+
+For studies involving privacy or safety controls on public access to the data, this section should describe in detail these controls, including how authors can apply to access the data, what criteria will be used to determine who may access the data, and any limitations on data use.
+
+\section*{Code availability}
+
+For all studies using custom code in the generation or processing of datasets, a statement must be included under the heading "Code availability", indicating whether and how the code can be accessed, including any restrictions to access.
+This section should also include information on the versions of any software used, if relevant, and any specific variables or parameters used to generate, test, or process the current dataset.
+
+\bibliography{sample}
+
+\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu.
+Use the cite command for an inline citation, e.g.
+\cite{Kaufman2020, Figueredo:2009dg, Babichev2002, behringer2014manipulating}.
+For data citations of datasets uploaded to e.g.
+\emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.
+For journal articles, DOIs should be included for works in press that do not yet have volume or page numbers.
+For other journal articles, DOIs should be included uniformly for all articles or not at all.
+We recommend that you encode all DOIs in your bibtex database as full URLs, e.g.
+https://doi.org/10.1007/s12110-009-9068-2.
+
+\section*{Acknowledgements} (not compulsory)
+
+Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
+
+\section*{Author contributions statement}
+
+Must include all authors, identified by initials, for example:
+A.A. conceived the experiment(s), A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results. All authors reviewed the manuscript.
+
+\section*{Competing interests} (mandatory statement)
+
+The corresponding author is responsible for providing a \href{https://www.nature.com/sdata/policies/editorial-and-publishing-policies#competing}{competing interests statement} on behalf of all authors of the paper.
+This statement must be included in the submitted article file.
+
+\section*{Figures \& Tables}
+
+Figures, tables, and their legends, should be included at the end of the document.
+Figures and tables can be referenced in \LaTeX{} using the ref command, e.g.
+Figure \ref{fig:stream} and Table \ref{tab:example}.
+
+Authors are encouraged to provide one or more tables that provide basic information on the main ‘inputs’ to the study (e.g.
+samples, participants, or information sources) and the main data outputs of the study.
+Tables in the manuscript should generally not be used to present primary data (i.e.
+measurements).
+Tables containing primary data should be submitted to an appropriate data repository.
+
+Tables may be provided within the \LaTeX{} document or as separate files (tab-delimited text or Excel files).
+Legends, where needed, should be included here.
+Generally, a Data Descriptor should have fewer than ten Tables, but more may be allowed when needed.
+Tables may be of any size, but only Tables which fit onto a single printed page will be included in the PDF version of the article (up to a maximum of three).
+
+Due to typesetting constraints, tables that do not fit onto a single A4 page cannot be included in the PDF version of the article and will be made available in the online version only.
+Any such tables must be labelled in the text as ‘Online-only’ tables and numbered separately from the main table list e.g.
+‘Table 1, Table 2, Online-only Table 1’ etc.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{./assets/stream}
+\caption{Legend (350 words max). Example legend text.}
+\label{fig:stream}
+\end{figure}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+Condition & n & p \\
+\hline
+A & 5 & 0.1 \\
+\hline
+B & 10 & 0.01 \\
+\hline
+\end{tabular}
+\caption{\label{tab:example}Legend (350 words max). Example legend text.}
+\end{table}
+
 \end{document}

### 2023-08-04 draft/v1.tex
Wrote a background summary.

--- 2023-08-02 draft/v1.tex
@@
-\documentclass{article}
+\documentclass[fleqn,10pt]{wlscirep}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{lineno}
+\linenumbers
+
+\title{A Comprehensive Dataset of U.S. Laws }
+
+\author[$\dag$]{Brian Libgober}
+\affil[$\dag$]{Northwestern University, Department of Political Science and School of Law, Evanston, IL, 60202, USA. brian.libgober@northwestern.edu}
+
+\begin{abstract}
+Lists of US laws figure importantly in many research projects in political science, law, sociology, economics, and other disciplines.
+Yet despite their prominence and frequent use, there is no authoritative and complete dataset of all US laws.
+In part, this is because US laws have been enacted over hundreds of years, resulting in a complicated patchwork published in numerous and inconsistent formats.
+As a simplification, many scholars have relied upon more selective lists of \textit{major} legislative enactments, although the selection criteria for these narrower lists make their use questionable in many cases.
+Here, we describe our efforts to create a complete database of US laws and their revision histories by combining data from HEINOnline and Congress.gov.
+\end{abstract}
 
@@
 
-Something
+\flushbottom
+\maketitle
+%  Click the title above to edit the author information and abstract
+
+\thispagestyle{empty}
+
+\section*{Background \& Summary}
+
+%(700 words maximum) An overview of the study design, the assay(s) performed, and the created data, including any background information needed to put this study in the context of previous work and the literature.
+The section should also briefly outline the broader goals that motivated the creation of this dataset and the potential reuse value.
+We also encourage authors to include a figure that provides a schematic overview of the study and assay(s) design.
+The Background \& Summary should not include subheadings.
+This section and the other main body sections of the manuscript should include citations to the literature as needed.
+
+In the US federal system, laws in the sense of ordinary usage can originate from many sources, including Courts, the President, agencies, and so forth.
+Yet when scholars speak more formally about the set of "US laws," they typically intend to refer to the set of authoritative documents enacted via the legislative process by the two chambers of the US Congress, with the possible input of the President.
+When Congress acts legislatively, it may do so by issuing a variety of documents that go by different names, have different formal features, and follow different processes.
+At present writing, the set of allowable actions include bills, joint resolutions, concurrent resolutions, and simple resolutions.
+Of these, only bills and joint resolutions have the general and binding character that one typically associates with laws.
+And even then, there are exceptions within these categories.
+"Private bills" granting relief in one-off cases are typically not what scholars have in mind when one refers to ``laws'', nor are joint resolutions approving constitutional amendments which are not ratified by the states (e.g.
+the Equal Rights Amendment) really laws.
+That said, the set of enacted bills and joint resolutions is a relatively precise definition of what scholars \textit{should} mean when they talk about the set of US federal laws.
+
+Studies of lawmaking in US political science are not new.
+Indeed, a very important debate in political science over the past several decades has to do with whether unified government, where the President and Congress are controlled by the same party, is better or worse for legislative productivity than divided government, where these organs are not exclusively in controlled by the same political party.
+This debate was initiated by Mayhew, who published a list of ``major'' legislative enactments identified by the set of laws that were mentioned in the editorial page of the New York Times and other prominent newspapers.
+This list of major enactments has been updated nearly annually since its original publication in DATE.
+Of course, the coverage of major legislative enactments is obviously limited as a database of all federal laws, both because it does not cover laws that fail to draw the attention of editorial pages, nor does it cover laws enacted before the existence of outlets such as the New York Times.
+Indeed, PERIOD COVERED.
+
+Addressing these weaknesses has been the subject of at least two other research projects.
+The Policy Agendas Project does X.
+Their focus on covering the subject matter of lawmaking is an important undertaking, although arduous, and it is unsurprising given the difficulties of this undertaking that they have only managed to cover X-Y.
+Ansolabhere Palmer Schneer devise novel methods for extending the list of major enactments backward in time.
+DESCRIBE HOW THEY DO IT.
+Still, their coverage is hardly exhaustive.
+
+There are several reasons why it is desirable to have a more complete dataset of US lawmaking than has previously existed.
+In particular, minor legislation is usually major to somebody, otherwise they would not go through the trouble of passing it.
+While focusing on the big pieces of legislation is perhaps appropriate for thinking about how party control effects the ability of collective government to solve the big problems, a more granular perspective is really necessary to think about how special interests may whittle away the gains made by broad coalitions through smaller pieces of legislation, or perhaps how policy fails to make the necessary incremental adjustments to keep with the times.
+The lack of a unified and complete dataset also frustrates progress of the discipline, as these authors do not necessarily use the same system to refer to particular laws, making US law datasets used by social scientist less interoperable than they should be.
+
+Our project seeks to build a comprehensive and easily updated list of US laws and their revision histories based on publicly available sources.
+The two key sources we leverage are the Statutes at Large, for laws existing before 2012, and Congress.gov, for more recent laws.
+The Congress.gov component is downloadable by webscraping and is relatively uncomplicated.
+The more challenging part of the project involves cataloguing the older set of laws contained within the Statutes at Large.
+Surprisingly, the US government does not make electronic copies of the Statutes at Large available prior to 1951,\footnote{https://www.govinfo.gov/app/collection/statute/2016}, despite the fact that there were 64 earlier volumes containing laws that in many cases have not been amended, for example the law from the 1870s that formed the basis of an indicment against Donald Trump for ``conspiracy against rights.'' Despite the surprising limited availability of these foundational documents, a database widely used by legal scholars, HeinOnline, has digitized all these books in their entirety and provided meta data on their table of contents.
+Laws are identified in the statutes of laws in various and not perfectly ways across the decades.
+For this reason, we supply a more consistent set of identifiers that, going forward, allows laws to be easily matched by researchers.
+Additionally, we include a set of text data that corresponds to these laws, although particularly for earlier laws these will be collected via OCR.
+
+\section*{Methods}
+
+% The Methods should include detailed text describing any steps or procedures used in producing the data, including full descriptions of the experimental design, data acquisition assays, and any computational processing (e.g.
+normalization, image feature extraction).
+See the detailed section in our submission guidelines for advice on writing a transparent and reproducible methods section.
+Related methods should be grouped under corresponding subheadings where possible, and methods should be described in enough detail to allow other researchers to interpret and repeat, if required, the full study.
+Specific data outputs should be explicitly referenced via data citation (see Data Records and Citing Data, below).
+
+% Authors should cite previous descriptions of the methods under use, but ideally the method descriptions should be complete enough for others to understand and reproduce the methods and processing steps without referring to associated publications.
+There is no limit to the length of the Methods section.
+Subheadings should not be numbered.
+
+% \subsection*{Subsection}
+
+% Example text under a subsection. Bulleted lists may be used where appropriate, e.g.
+
+% \begin{itemize}
+% \item First item
+% \item Second item
+% \end{itemize}
+
+% \subsubsection*{Third-level section}
+
+% Topical subheadings are allowed.
+
+\section*{Data Records}
+
+% The Data Records section should be used to explain each data record associated with this work, including the repository where this information is stored, and to provide an overview of the data files and their formats.
+Each external data record should be cited numerically in the text of this section, for example \cite{Hao:gidmaps:2014}, and included in the main reference list as described below.
+A data citation should also be placed in the subsection of the Methods containing the data-collection or analytical procedure(s) used to derive the corresponding record.
+Providing a direct link to the dataset may also be helpful to readers (\hyperlink{https://doi.org/10.6084/m9.figshare.853801}{https://doi.org/10.6084/m9.figshare.853801}).
+
+% Tables should be used to support the data records, and should clearly indicate the samples and subjects (study inputs), their provenance, and the experimental manipulations performed on each (please see 'Tables' below).
+They should also specify the data output resulting from each data-collection or analytical step, should these form part of the archived record.
+
+\section*{Technical Validation}
+
+% This section presents any experiments or analyses that are needed to support the technical quality of the dataset.
+This section may be supported by figures and tables, as needed.
+This is a required section; authors must present information justifying the reliability of their data.
+
+\section*{Usage Notes}
+
+% The Usage Notes should contain brief instructions to assist other researchers with reuse of the data.
+This may include discussion of software packages that are suitable for analysing the assay data files, suggested downstream processing steps (e.g.
+normalization, etc.), or tips for integrating or comparing the data records with other datasets.
+Authors are encouraged to provide code, programs or data-processing workflows if they may help others understand or use the data.
+Please see our code availability policy for advice on supplying custom code alongside Data Descriptor manuscripts.
+
+% For studies involving privacy or safety controls on public access to the data, this section should describe in detail these controls, including how authors can apply to access the data, what criteria will be used to determine who may access the data, and any limitations on data use.
+
+\section*{Code availability}
+
+% For all studies using custom code in the generation or processing of datasets, a statement must be included under the heading "Code availability", indicating whether and how the code can be accessed, including any restrictions to access.
+This section should also include information on the versions of any software used, if relevant, and any specific variables or parameters used to generate, test, or process the current dataset.
+
+\bibliography{sample}
+
+% \noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu.
+Use the cite command for an inline citation, e.g.
+\cite{Kaufman2020, Figueredo:2009dg, Babichev2002, behringer2014manipulating}.
+For data citations of datasets uploaded to e.g.
+\emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.
+For journal articles, DOIs should be included for works in press that do not yet have volume or page numbers.
+For other journal articles, DOIs should be included uniformly for all articles or not at all.
+We recommend that you encode all DOIs in your bibtex database as full URLs, e.g.
+https://doi.org/10.1007/s12110-009-9068-2.
+
+\section*{Acknowledgements} (not compulsory)
+
+% Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
+
+\section*{Author contributions statement}
+
+% Must include all authors, identified by initials, for example:
+% A.A. conceived the experiment(s), A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results. All authors reviewed the manuscript.
+
+\section*{Competing interests} (mandatory statement)
+
+% The corresponding author is responsible for providing a \href{https://www.nature.com/sdata/policies/editorial-and-publishing-policies#competing}{competing interests statement} on behalf of all authors of the paper.
+This statement must be included in the submitted article file.
+
+\section*{Figures \& Tables}
+
+% Figures, tables, and their legends, should be included at the end of the document.
+Figures and tables can be referenced in \LaTeX{} using the ref command, e.g.
+Figure \ref{fig:stream} and Table \ref{tab:example}.
+
+% Authors are encouraged to provide one or more tables that provide basic information on the main ‘inputs’ to the study (e.g.
+samples, participants, or information sources) and the main data outputs of the study.
+Tables in the manuscript should generally not be used to present primary data (i.e.
+measurements).
+Tables containing primary data should be submitted to an appropriate data repository.
+
+% Tables may be provided within the \LaTeX{} document or as separate files (tab-delimited text or Excel files).
+Legends, where needed, should be included here.
+Generally, a Data Descriptor should have fewer than ten Tables, but more may be allowed when needed.
+Tables may be of any size, but only Tables which fit onto a single printed page will be included in the PDF version of the article (up to a maximum of three).
+
+% Due to typesetting constraints, tables that do not fit onto a single A4 page cannot be included in the PDF version of the article and will be made available in the online version only.
+Any such tables must be labelled in the text as ‘Online-only’ tables and numbered separately from the main table list e.g.
+‘Table 1, Table 2, Online-only Table 1’ etc.
+
+% \begin{figure}[ht]
+% \centering
+% \includegraphics[width=\linewidth]{./assets/stream}
+% \caption{Legend (350 words max). Example legend text.}
+% \label{fig:stream}
+% \end{figure}
+
+% \begin{table}[ht]
+% \centering
+% \begin{tabular}{|l|l|l|}
+% \hline
+% Condition & n & p \\
+% \hline
+% A & 5 & 0.1 \\
+% \hline
+% B & 10 & 0.01 \\
+% \hline
+% \end{tabular}
+% \caption{\label{tab:example}Legend (350 words max). Example legend text.}
+% \end{table}
+
 \end{document}

### 2023-08-10 reference/scriptforggplot1.R
R ggplots for differences between law counts

@@ -1,0 +1,59 @@
+#allow multiple users to access
+if (Sys.getenv("USER") == 'brianlibgober'){
+  setwd("~/Downloads/")
+} else {
+  setwd("/Users/jamiegall/Desktop/")
+}
+
+#libraries
+library(readxl)
+library(dplyr)
+library(tidyverse)
+library(tidyr)
+library(ggplot2)
+
+#load data
+count_of_acts <- read_excel("count_of_acts.xlsx")
+
+#rename
+count_of_acts <- count_of_acts %>%
+  rename(galloway_count = "Galloway Counts")
+count_of_acts <- count_of_acts %>%
+  rename(lib_count = "n")
+
+#plot of data
+pl <- ggplot(data = count_of_acts, aes(x = congress_number)) +
+  geom_line(aes(y = lib_count, color = "Lib Count"), size = 0.5) +
+  geom_path(aes(y = galloway_count, color = "Galloway Count"), size = 1, linetype = "22") +  # Dashed line
+  theme_classic() +
+  ylab("Count") +
+  scale_color_manual(values = c("Lib Count" = "blue", "Galloway Count" = "red")) +
+  labs(color = "Variable") +  # Legend title
+  theme(legend.position = "bottom",  # Move the legend to the bottom
+        plot.margin = margin(t = 20, r = 20, b = 50, l = 20, unit = "pt"))+  # Adjust margins
+  scale_y_log10()  # Apply logarithmic scale
+print(pl)
+
+#make difference column
+count_of_acts$difference <-  count_of_acts$galloway_count - count_of_acts$lib_count
+
+#plot difference data
+pl2 <- ggplot(data = count_of_acts, aes(x = congress_number)) +
+  geom_line(aes(y = difference)) +
+  theme_classic() +
+  ylab("Difference")
+print(pl2)
+
+#make a percentage error column
+count_of_acts$pctdifference <-  (count_of_acts$galloway_count / count_of_acts$lib_count) * 100
+
+#percentage error ggplot
+pl3 <- ggplot(data = count_of_acts, aes(x = congress_number)) +
+  geom_line(aes(y = pctdifference)) +
+  theme_classic() +
+  coord_cartesian(ylim = c(95, 105)) +
+  ylab("Percent Ratio Galloway/Libgober")
+
+print(pl3)
+
+ 

### 2023-08-10 draft/v1.tex

@@
 In the US federal system, laws in the sense of ordinary usage can originate from many sources, including Courts, the President, agencies, and so forth.
-Yet when scholars speak more formally about the set of "US laws," they typically intend to refer to the set of authoritative documents enacted via the legislative process by the two chambers of the US Congress, with the possible input of the President.
+Yet when scholars speak more formally about the set of "US laws," they typically intend to refer to the set of authoritative documents enacted by the two chambers of the US Congress by following the legislative process.
 When Congress acts legislatively, it may do so by issuing a variety of documents that go by different names, have different formal features, and follow different processes.
@@
 And even then, there are exceptions within these categories.
-"Private bills" granting relief in one-off cases are typically not what scholars have in mind when one refers to ``laws'', nor are joint resolutions approving constitutional amendments which are not ratified by the states (e.g.
+``Private bills" granting relief in one-off cases\footnote{For example, last year Congress enacted a private law allowing Alaska-woman Rebecca Trimble to obtain permanent resident status, despite the fact the paperwork her adoptive parents had used to bring her to the United States from Mexico had been defective.} are typically not what scholars have in mind when one refers to ``laws'', nor are joint resolutions approving constitutional amendments which are not ratified by the states (e.g.
 the Equal Rights Amendment) really laws.
@@
 Indeed, a very important debate in political science over the past several decades has to do with whether unified government, where the President and Congress are controlled by the same party, is better or worse for legislative productivity than divided government, where these organs are not exclusively in controlled by the same political party.
-This debate was initiated by Mayhew, who published a list of ``major'' legislative enactments identified by the set of laws that were mentioned in the editorial page of the New York Times and other prominent newspapers.
-This list of major enactments has been updated nearly annually since its original publication in DATE.
-Of course, the coverage of major legislative enactments is obviously limited as a database of all federal laws, both because it does not cover laws that fail to draw the attention of editorial pages, nor does it cover laws enacted before the existence of outlets such as the New York Times.
-Indeed, PERIOD COVERED.
+This debate was initiated by Mayhew (1991) \nocite{Mayhew1991}, who published a list of ``major'' legislative enactments identified by the set of laws that were mentioned in the editorial page of the New York Times and other prominent newspapers.
+This list of major enactments has been updated annually since its original publication in 1991 and is, at present writing, current from 1947 through 2022.
+Of course, the coverage of major legislative enactments is obviously limited as a database of all federal laws, both because it does not cover laws that fail to draw the attention of editorial pages, nor does it cover laws enacted during the New Deal or earlier.
 
-Addressing these weaknesses has been the subject of at least two other research projects.
-The Policy Agendas Project does X.
-Their focus on covering the subject matter of lawmaking is an important undertaking, although arduous, and it is unsurprising given the difficulties of this undertaking that they have only managed to cover X-Y.
-Ansolabhere Palmer Schneer devise novel methods for extending the list of major enactments backward in time.
-DESCRIBE HOW THEY DO IT.
-Still, their coverage is hardly exhaustive.
+Addressing these weaknesses has been the subject of at least two other major research projects.
+The Policy Agendas Project is a long-standing collaborative research effort aimed at building multiple datasets for tracking and comparing which issues manage to attract the attention of government across.
+It covers many national and subnatnional systems, including hte United States federal government.
+In particular, their database of bills covers "more than 400,000 bills introduced by the US Congress." Importantly, they also have coded each bill according to the subject-matter coding system of the larger Policy Agenda Project.
+Their focus on covering the subject matter of lawmaking is an important undertaking, although arduous, and it is unsurprising given the difficulties of this undertaking that they have only managed to cover the period 1947-2022.
+The second project with relevant and similar prior data collection is due to Ansolabehere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016,ansolabehere2018divided} Their data collection, which was conducted under the auspices of an undergraduate course at Harvard called ``"What Has Congress Done," crowd-sourced the task of identifying significant legislation to students, each of whom was responsible for producing a list of significant legislation enacted under each of 22 potentially assigned decades.
+The researchers provided a list of secondary sources, as well as guidance and quality control efforts.
+Similar to Mayhew, their criteria for inclusion were (a) was the law considered significant at the time of enactment, and (b) does the law seem significant in historical perspective.
+Because of their differing methods, the two sources do not completely overlap in the 1947-2022 period.
+Although the temporal coverage for the Ansolabehere, Palmer, and Schneer dataset is very comprehensive, it contains a small percentage of all laws enacted by the US Congress.
+
+% A few OTHER PAPERS
+% Clinton and Lapinski (2006)
+% Stathis (2014)
+% Howell, William, Scott Adler, Charles Cameron, and Charles Riemann (2000) “Divided government
+and the legislative productivity of Congress, %1945–94.” Legislative Studies Quarterly 25 (2): 285–
+%312
 
@@
 While focusing on the big pieces of legislation is perhaps appropriate for thinking about how party control effects the ability of collective government to solve the big problems, a more granular perspective is really necessary to think about how special interests may whittle away the gains made by broad coalitions through smaller pieces of legislation, or perhaps how policy fails to make the necessary incremental adjustments to keep with the times.
-The lack of a unified and complete dataset also frustrates progress of the discipline, as these authors do not necessarily use the same system to refer to particular laws, making US law datasets used by social scientist less interoperable than they should be.
+There is notable inconsistency in what laws are included as significant using all these methods.
+The lack of a unified and complete dataset also frustrates progress of the discipline, as these authors do not necessarily use the same system to refer to particular laws, making US law datasets used by social scientist less inter-operable than they should be.
 
@@
 The more challenging part of the project involves cataloguing the older set of laws contained within the Statutes at Large.
-Surprisingly, the US government does not make electronic copies of the Statutes at Large available prior to 1951,\footnote{https://www.govinfo.gov/app/collection/statute/2016}, despite the fact that there were 64 earlier volumes containing laws that in many cases have not been amended, for example the law from the 1870s that formed the basis of an indicment against Donald Trump for ``conspiracy against rights.'' Despite the surprising limited availability of these foundational documents, a database widely used by legal scholars, HeinOnline, has digitized all these books in their entirety and provided meta data on their table of contents.
+Surprisingly, the US government does not make electronic copies of the Statutes at Large available prior to 1951,\footnote{https://www.govinfo.gov/app/collection/statute/2016}, despite the fact that there were 64 earlier volumes containing laws that in many cases have not been amended.
+Despite the surprising limited availability of these foundational documents, a database widely used by legal scholars, HeinOnline, has digitized all these books in their entirety and provided meta data on their table of contents.
 Laws are identified in the statutes of laws in various and not perfectly ways across the decades.
 For this reason, we supply a more consistent set of identifiers that, going forward, allows laws to be easily matched by researchers.
-Additionally, we include a set of text data that corresponds to these laws, although particularly for earlier laws these will be collected via OCR.
+We describe these identifiers in more detail in the usage section below.
+Additionally, we include a set of text data that corresponds to these laws, although particularly for earlier laws these are collected via OCR.
 
 \section*{Methods}
+
+We rely on two primary sources for our comprehensive database of US laws: the U.S. Statutes at Large, as disseminated via HeinOnline, and Congress.gov.
+
+For our data collection based on HeinOnline, we began by scraping the table of contents of each volume of the statues at large, excepting volumes 6-8 which contain a collection of early treaties and private laws.
+Examination of these tables reveals that laws are identified using various citation systems depending on era.
+In particular,
+
+\begin{itemize}
+\item The currently practiced identification system begins on Jan 7, 1959 with the 86th Congress.
+In this system, laws are identified by the number of the Congress and the law number within Congress.
+An example is ``Public Law 105-89, An Act: to promote the adoption of children in foster care.''
+\item Initially, laws were identified by a different system.
+From the 1st through the 56th Congress, which concluded March 3, 1901, laws were identified in the Statutes at Large by chapter as well as Congress and session (e.g.
+``Chapter 15, 56 Congress, Session 1, An Act: Relating to Cuban vessels.")
+\item For the 57th through 85th congress, the Statutes at Large inconsistently use both systems, with the important caveat that chapters and public laws are sometimes recycled over the two sessions of a particular Congress.\footnote{Or worse, the same session.
+Indeed, PL 65-246 refers to both a law ``Providing for the transportation from the District of Columbia of governmental employees whose services no longer are required." and also a law intended ``To authorize the sale of certain lands to school district numbered twenty-eight, of Missoula County, Montana."} Careful attention to chapters, public laws, and sessions does disambiguate all laws, however these details are very particular and subtle.
+\end{itemize}
+
+Following these citation practices, we used a rule-based parser to extract key pieces of information to identify the law.
+Technical validation efforts revealed that there were occasional errors of transcription in our source data, for example mis-identification of chapters associated with laws or including page numbers that were not correct.
+Those errors that were found in the source data we corrected to conform with the text image captured on the HeinOnline site.
 
@@
 
-\section*{Usage Notes}
+We offer two primary approaches to support the technical validation of our dataset.
+The first is to compare the total counts of laws by Congress against previously published totals while the second validation exercise is to show that all of the laws described in five distinct sources of major laws are, indeed, present in our dataset.
+
+The reference counts for total laws that we rely on comes from Appendix F reported in Galloway and Wise's History of the House of Representatives, and also previously used for validation and analysis by Ansolabhere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016} Our definition of law is slightly more capacious than theirs, in the sense that we also consider "Joint Resolutions" laws, and the authors admit their own counts combine acts and resolutions (the latter of which are not, in our view, best understood as laws) from the 77th Congress and after.
+Figure \ref{fig:totals} compares the counts for this key subset of our data.
+Note that the total deviation in counts is X.
+An undergraduate research assistant further investigated the difference in counts of laws in Congress A and B.
+In both cases, the number of laws that the research assistant counted in that Congress was the same as the number we provided.
+
+A second 
+\
+
+\section*{Usage Notes}  \label{sec:usage}
 
@@
 
-\bibliography{sample}
+\bibliography{biblio}
 

### 2023-08-10 analysis/scriptforggplot1.R
updated figures and added local files

@@ -1,0 +1,55 @@
+#libraries
+library(here)
+library(readxl)
+library(dplyr)
+library(tidyverse)
+library(tidyr)
+library(ggplot2)
+
+here::i_am("analysis/scriptforggplot1.R")
+
+#load data
+count_of_acts <- read_excel(here("build","count_of_acts.xlsx"))
+
+#rename
+count_of_acts <- count_of_acts %>%
+  rename(galloway_count = "Galloway Counts")
+count_of_acts <- count_of_acts %>%
+  rename(lib_count = "n")
+
+#plot of data
+pl <- ggplot(data = count_of_acts, aes(x = congress_number)) +
+  geom_line(aes(y = lib_count, color = "Lib Count"), size = 0.5) +
+  geom_path(aes(y = galloway_count, color = "Galloway & Wise"), size = 1, linetype = "22") +  # Dashed line
+  theme_classic() +
+  ylab("Number of Acts of Congress") +
+  scale_x_continuous('Congress',breaks=c(1,20,40,60,76)) + 
+  scale_color_manual(NULL,values = c("Author's Count" = "blue", "Galloway & Wise" = "red")) +
+  labs() +  # Legend title
+  theme(legend.position = "bottom") 
+print(pl)
+
+save(pl,file = here("draft","figures","counts_of_laws.png"))
+#make difference column
+count_of_acts$difference <-  count_of_acts$galloway_count - count_of_acts$lib_count
+
+#plot difference data
+pl2 <- ggplot(data = count_of_acts, aes(x = congress_number)) +
+  geom_line(aes(y = difference)) +
+  theme_classic() +
+  ylab("Difference")
+print(pl2)
+
+#make a percentage error column
+count_of_acts$pctdifference <-  (count_of_acts$galloway_count / count_of_acts$lib_count) * 100
+
+#percentage error ggplot
+pl3 <- ggplot(data = count_of_acts, aes(x = congress_number)) +
+  geom_line(aes(y = pctdifference)) +
+  theme_classic() +
+  coord_cartesian(ylim = c(95, 105)) +
+  ylab("Percent Ratio Galloway/Libgober")
+
+print(pl3)
+
+ 

### 2023-08-10 build/heinonline/main.py

@@ -1,0 +1,194 @@
+# -*- coding: utf-8 -*-
+"""
+@Author Brian Libgober
+@Date August 6, 2023
+
+"""
+
+#%%
+import requests
+import tqdm
+import subprocess
+from parsel import Selector
+import urllib
+import regex as re
+import pandas as pd
+import pendulum
+#%%
+
+def parse_toc(i):
+    """
+    Takes a volume number of the Statutes at Large and extracts directory data    
+
+    Parameters
+    ----------
+    i : integer
+        Volume number.
+
+    Returns
+    -------
+    directory_data : list of dicts.
+        A list of directory data
+    """
+    with open("heinonline_tocs/" + str(i) + '.html',"r") as o:
+        raw  = o.read()
+    s = Selector(raw)
+    law_descriptors = s.xpath("//ul[@class='dropdown-submenu']//li")
+    directory_data = []
+    for law in law_descriptors:
+        directory_data.append(parse_law_html(law,i))
+    return(directory_data)
+
+def parse_law_html(law,volume):
+    """
+    Extracts relevant metadata from a table of contents entry.
+
+    Parameters
+    ----------
+    law : parsel.selector.Selector
+        An entry from the table of contents from HeinOnline.
+    volume : int 
+        Volume of Statutes at Large, since citation style depends on era
+
+    Returns
+    -------
+    out : dict
+        Values of the meta data
+
+    """
+    #create a container for output
+    out = {'sal_volume' : volume}
+    #extract the raw components
+    raw_date = law.xpath("./div/i/text()").\
+            extract_first().\
+                replace(".","").\
+                strip().\
+                strip("-").\
+                strip()
+    raw_description = law.xpath("./div/text()").extract_first().strip()
+    #more meta data for additoinal scraping, i.e. page length
+    page_handle_url = law.xpath(
+        "./div/div[@class='page_line']/a[@class='contents_page']/@href").\
+        extract_first()
+    try:
+        out['hol_id'] = urllib.parse.parse_qs(page_handle_url)['id'][0]
+    except:
+        pass
+    
+    out['sal_page_start'] = law.xpath(
+        "./div/div[@class='page_line']/a[@class='contents_page']/i/text()").\
+        extract_first().\
+        strip().\
+        strip("Page").\
+        strip()
+    #parse the date
+    try:
+        out['date'] = pendulum.\
[…]

### 2023-08-10 validate/validate_hein.R

@@ -1,0 +1,181 @@
+library(tidyverse)
+library(lubridate)
+all_laws = read_csv("heinonline/hein_data_raw.csv")
+errors = read_csv("heinonline/hein_errors.csv") %>%
+  mutate(date=parse_date_time(date,orders=c('%Y-%m-%d','mdy')))
+
+tmp1 = all_laws %>%
+  left_join(errors) %>%
+  mutate(chapter=ifelse(is.na(new_chapter),chapter,new_chapter)) %>%
+  select(-new_chapter)
+
+
+acts = tmp1 %>%
+  filter(action %in% c("An Act"))
+
+
+
+acts %>%
+  filter(is.na(sal_page_start)) %>% 
+  write.csv("heinonline/missing_sal_page.csv")
+
+# Validation
+
+pre.57 = acts %>%
+  filter(congress_number<57) 
+
+#
+number.of.non.unique.entries = pre.57 %>%
+  group_by(congress_number,
+           session_number,
+           chapter) %>%
+  count() %>%
+  filter(n>1) %>%
+  nrow()
+
+pre.57.chapter.counts = pre.57 %>%
+  group_by(congress_number,
+           session_number)  %>%
+  summarise(n.chapters = max(chapter))
+
+middle.
+
+
+pre.57.expected.chapters = pre.57.chapter.counts %>%
+  cross_join(data.frame(
+    chapter=1:(pre.57.chapter.counts$n.chapters %>% max())
+  )) %>%
+  filter(chapter<=n.chapters) %>%
+  select(-n.chapters)
+
+gaps = pre.57.expected.chapters %>%
+  left_join(pre.57) %>%
+  filter(is.na(sal_page_start)) %>%
+  select(congress_number:chapter) 
+
+gaps %>%
+  group_by(congress_number,session_number) %>%
+  mutate(lead(chapter))
+
+gaps %>%
+  mutate(some.follows=lead(chapter)==chapter+1,
+         some.precedes=lag(chapter)==chapter-1) %>%
+  filter(!(some.follows & some.precedes))
+
+
+volumes.of.congress.sessions = pre.57 %>%
+  select(congress_number,session_number,sal_volume) %>%
+  distinct()
+
+#https://mattboegner.com/improve-your-sql-skills-master-the-gaps-islands-problem/
+gaps.to.check = pre.57.expected.chapters %>%
+  left_join(pre.57)  %>%
+  select(-date,-hol_id,-action,-title,-pl_no) %>%
[…]

### 2023-08-10 draft/v1.tex

@@
 
-The reference counts for total laws that we rely on comes from Appendix F reported in Galloway and Wise's History of the House of Representatives, and also previously used for validation and analysis by Ansolabhere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016} Our definition of law is slightly more capacious than theirs, in the sense that we also consider "Joint Resolutions" laws, and the authors admit their own counts combine acts and resolutions (the latter of which are not, in our view, best understood as laws) from the 77th Congress and after.
+The reference counts for total laws that we rely on comes from Appendix F reported in Galloway and Wise's History of the House of Representatives\nocite{gallowaywise}, and also previously used for validation and analysis by Ansolabhere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016} Our definition of law is slightly more capacious than Galloway and Wise's, in the sense that we also consider "Joint Resolutions" laws, and the authors admit their own counts combine acts and resolutions (the latter of which are not, in our view, best understood as laws) from the 77th Congress and after.
 Figure \ref{fig:totals} compares the counts for this key subset of our data.
-Note that the total deviation in counts is X.
+Note that the total deviation in counts is 3.
 An undergraduate research assistant further investigated the difference in counts of laws in Congress A and B.
@@
 
+\begin{figure}[htbp]
+  \centering
+  \begin{subfigure}{0.4\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{draft/figures/.jpg}
+    \caption{Caption for Figure 1}
+    \label{fig:subfig1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.4\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure2.jpg}
+    \caption{Caption for Figure 2}
+    \label{fig:subfig2}
+  \end{subfigure}
+  \caption{Comparing the count of laws between Galloway \& Wise's Appendix F to the equivalent subset of this paper's replication data.}
+  \label{fig:main}
+\end{figure}
+
 A second
-\
 

### 2023-08-10 analysis/scriptforggplot1.R
yo

@@ -29,7 +29,7 @@ pl <- ggplot(data = count_of_acts, aes(x = congress_number)) +
   theme(legend.position = "bottom") 
 print(pl)
 
-save(pl,file = here("draft","figures","counts_of_laws.png"))
+save(pl,file = here("draft","figures","counts_of_laws.jpg"))
 #make difference column
 count_of_acts$difference <-  count_of_acts$galloway_count - count_of_acts$lib_count
 
@@ -41,15 +41,23 @@ pl2 <- ggplot(data = count_of_acts, aes(x = congress_number)) +
 print(pl2)
 
 #make a percentage error column
-count_of_acts$pctdifference <-  (count_of_acts$galloway_count / count_of_acts$lib_count) * 100
+count_of_acts$pctdifference <-  (count_of_acts$lib_count / count_of_acts$galloway_count) - 1
 
 #percentage error ggplot
 pl3 <- ggplot(data = count_of_acts, aes(x = congress_number)) +
   geom_line(aes(y = pctdifference)) +
   theme_classic() +
-  coord_cartesian(ylim = c(95, 105)) +
-  ylab("Percent Ratio Galloway/Libgober")
+  scale_y_continuous(limits=c(-0.025, .025),labels = scales::percent_format()) + 
+  ylab("Percentage Discrepancy Relative to Galloway & Wise") + 
+  scale_x_continuous('Congress',breaks=c(1,20,40,60,76)) 
+
+save(pl3,file = here("draft","figures","discrpency.jpg"))
 
 print(pl3)
+
+
+count_of_acts %>%
+  summarise(sum(galloway_count),sum(lib_count),sum(abs(lib_count-galloway_count)),
+            sum(abs(lib_count-galloway_count)>0))
 
  

### 2023-08-10 reference/scriptforggplot1.R

@@ -1,59 +1,0 @@
-#allow multiple users to access
-if (Sys.getenv("USER") == 'brianlibgober'){
-  setwd("~/Downloads/")
-} else {
-  setwd("/Users/jamiegall/Desktop/")
-}
-
-#libraries
-library(readxl)
-library(dplyr)
-library(tidyverse)
-library(tidyr)
-library(ggplot2)
-
-#load data
-count_of_acts <- read_excel("count_of_acts.xlsx")
-
-#rename
-count_of_acts <- count_of_acts %>%
-  rename(galloway_count = "Galloway Counts")
-count_of_acts <- count_of_acts %>%
-  rename(lib_count = "n")
-
-#plot of data
-pl <- ggplot(data = count_of_acts, aes(x = congress_number)) +
-  geom_line(aes(y = lib_count, color = "Lib Count"), size = 0.5) +
-  geom_path(aes(y = galloway_count, color = "Galloway Count"), size = 1, linetype = "22") +  # Dashed line
-  theme_classic() +
-  ylab("Count") +
-  scale_color_manual(values = c("Lib Count" = "blue", "Galloway Count" = "red")) +
-  labs(color = "Variable") +  # Legend title
-  theme(legend.position = "bottom",  # Move the legend to the bottom
-        plot.margin = margin(t = 20, r = 20, b = 50, l = 20, unit = "pt"))+  # Adjust margins
-  scale_y_log10()  # Apply logarithmic scale
-print(pl)
-
-#make difference column
-count_of_acts$difference <-  count_of_acts$galloway_count - count_of_acts$lib_count
-
-#plot difference data
-pl2 <- ggplot(data = count_of_acts, aes(x = congress_number)) +
-  geom_line(aes(y = difference)) +
-  theme_classic() +
-  ylab("Difference")
-print(pl2)
-
-#make a percentage error column
-count_of_acts$pctdifference <-  (count_of_acts$galloway_count / count_of_acts$lib_count) * 100
-
-#percentage error ggplot
-pl3 <- ggplot(data = count_of_acts, aes(x = congress_number)) +
-  geom_line(aes(y = pctdifference)) +
-  theme_classic() +
-  coord_cartesian(ylim = c(95, 105)) +
-  ylab("Percent Ratio Galloway/Libgober")
-
-print(pl3)
-
- 

### 2023-08-10 draft/v1.tex
Updates from Overleaf

@@
 \usepackage{lineno}
+\usepackage{subcaption}
 \linenumbers
@@
 Figure \ref{fig:totals} compares the counts for this key subset of our data.
-Note that the total deviation in counts is 3.
+Note that in total Galloway and Wise count 23,155 laws while we would peg the figure at 23,152, a total difference of 3 laws ($\approx 0.13\%$ of the total).
+The true discrepancy is somewhat greater, as the Figure reveals, because in some years our counts are higher than Galloway \& Wise's, however in all but six Congresses our counts are identical.
+Summing up the absolute value of the difference in counts in these six Congresses, we arrive at a total difference of 11.
 An undergraduate research assistant further investigated the difference in counts of laws in Congress A and B.
@@
 
-\begin{figure}[htbp]
+\begin{figure}
     \centering
-  \begin{subfigure}{0.4\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{draft/figures/.jpg}
-    \caption{Caption for Figure 1}
-    \label{fig:subfig1}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.4\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure2.jpg}
-    \caption{Caption for Figure 2}
-    \label{fig:subfig2}
-  \end{subfigure}
-  \caption{Comparing the count of laws between Galloway \& Wise's Appendix F to the equivalent subset of this paper's replication data.}
-  \label{fig:main}
+    \includegraphics{draft/figures/counts_of_laws  
+    \caption{Caption}
+    \label{fig:enter-label}
 \end{figure}
-
 A second

### 2023-08-10 analysis/scriptforggplot1.R
fixed a ggsave error

@@ -29,7 +29,7 @@ pl <- ggplot(data = count_of_acts, aes(x = congress_number)) +
   theme(legend.position = "bottom") 
 print(pl)
 
-save(pl,file = here("draft","figures","counts_of_laws.jpg"))
+ggsave(pl,file = here("draft","figures","counts_of_laws.png"))
 #make difference column
 count_of_acts$difference <-  count_of_acts$galloway_count - count_of_acts$lib_count
 
@@ -51,7 +51,7 @@ pl3 <- ggplot(data = count_of_acts, aes(x = congress_number)) +
   ylab("Percentage Discrepancy Relative to Galloway & Wise") + 
   scale_x_continuous('Congress',breaks=c(1,20,40,60,76)) 
 
-save(pl3,file = here("draft","figures","discrpency.jpg"))
+ggsave(pl3,file = here("draft","figures","discrpency.png"))
 
 print(pl3)
 

### 2023-09-25 build/combine_sources.R
finalization checks

@@ -3,8 +3,13 @@ library(here)
 
 Mods = read_csv(here("build","mods.csv")) %>%
   mutate(Source="GPO")
-hein_data_raw =  read_csv(here("build","heinonline","hein_data_raw.csv")) %>%
+
+hein_data_raw =  read_csv(here("build","hein_data_raw.csv")) %>%
   mutate(Source="HeinOnline")
+
+nara_raw = stream_in(file(here("build","nara.jl")))   %>%
+  tibble()
+
 
 # cleaning inputs
 
@@ -26,6 +31,15 @@ mods_overlapping_periods = Mods %>%
     sal_volume>=65 ~ "Mid"
   ))
 
+
+
+nara = nara_raw 
+nara$pl_no = str_extract(nara$public_law,"\\d+\\-\\d+")
+nara$sal_volume = str_extract(nara$sal_citation, "(\\d+) Stat. (\\d+)",group=1) %>%
+  as.numeric()
+nara$sal_page_start = str_extract(nara$sal_citation, "(\\d+) Stat. (\\d+)",group=2) %>%
+  as.numeric()
+nara$date = mdy(nara$date)
 
 
 #%% now begin merging
@@ -173,13 +187,39 @@ Mods_new$dates_conflict <- NA
 Mods_new <- Mods_new %>%
   select(action, Title, sal_volume, sal_page_start, StatuteCitation, BillCitation, congress_number, chapter, session_number, pl_no, date_of_passage, secondary_date, dates_conflict, Source, URL )
 
+nara_new <- nara %>%
+  transmute(Title=title,
+         sal_volume,
+         sal_page_start,
+         StatuteCitation=sal_citation,
+         BillCitation=bill,
+         congress_number=congress,
+         session_number=session,
+         pl_no,
+         source="NARA")
+
 master = bind_rows(
   master_early_mid_and_late,
-  Mods_new
+  Mods_new,
+  nara_new
 ) %>%
   arrange(sal_volume, date_of_passage, secondary_date) %>%
   mutate(row_number = row_number()) %>%
-  select(row_number, action, Title, sal_volume, sal_page_start, StatuteCitation, BillCitation, congress_number, chapter, session_number, pl_no, date_of_passage, secondary_date, dates_conflict, Source, URL )
+  select(row_number, 
+         action, 
+         Title,
+         sal_volume, 
+         sal_page_start, 
+         StatuteCitation, 
+         BillCitation, 
+         congress_number,
+         chapter, 
[…]

### 2023-09-25 build/heinonline/main.py

@@ -188,7 +188,8 @@ def main(download_heinonline=False):
         download_heinonline_tocs()
     directory_data = process_tocs()
     hein_data_all = pd.DataFrame(directory_data)
-    hein_data_all.to_csv("hein_data_raw.csv",index=False)
+    out = hein_data_all[~hein_data_all.duplicated()]
+    out.to_csv("hein_data_raw.csv",index=False)
 #%%
     
 main()

### 2023-09-25 build/match_two_laws.R

@@ -1,4 +1,5 @@
 require(lubridate)
+require(assertthat)
 
 assign_regime <- function(date,congress_number){
   # first handle an error case where we cannot determine the reginme
@@ -33,12 +34,8 @@ assign_regime <- function(date,congress_number){
   return(regime)
 }
 
-assign_regime(bdl_laws$date_of_passage[1],bdl_laws$congress_number[1])
-assign_regime(bdl_laws$date_of_passage[1],100)
-
-merge_late_laws <- function(x,y,x.names,x.law_no,y.congress,y.law_no){
-  
-}
+#assign_regime(bdl_laws$date_of_passage[1],bdl_laws$congress_number[1])
+#assign_regime(bdl_laws$date_of_passage[1],100)
 
 
 assign_regime_with_named_arguments <- function(x,x.vars){
@@ -55,11 +52,6 @@ assign_regime_with_named_arguments <- function(x,x.vars){
     stop("Not enough data to determine appropriate citation regime")
   }
 }
-
-x.vars = list("date_of_passage"='date_of_passage',
-              "congress_number" = "congress_number")
-
-assign_regime_with_named_arguments(bdl_laws,list("congress_number" = "congress_number"))
 
 
 merge_late_regime_laws <- function(x.late,y.late,
@@ -89,8 +81,12 @@ merge_early_regime_laws <- function(x.early,y.early,
   "Assumes that the chapter,congress, session columns are validated"
   merged.early = merge(x.early,
                       y.early,
-                      by.x=x.vars[["pl_no"]],
-                      by.y=y.vars[["pl_no"]],
+                      by.x=c(x.vars[["congress_number"]],
+                             x.vars[["session"]],
+                             x.vars[["chapter"]]),
+                      by.y=c(y.vars[["congress_number"]],
+                             y.vars[["session"]],
+                             y.vars[["chapter"]]),
                       all.x=all.x,
                       all.y=all.y)
   
@@ -102,20 +98,75 @@ merge_middle_regime_laws <- function(x.middle,y.middle,
                                      y.vars,
                                      all.x,
                                      all.y){
+  "Assumes that the congres,session, and chapter are clean.
+  The merge will default to adding .y to the right hand dataset."
+  x.middle$x.ids = 1:nrow(x.middle)
[…]

### 2023-09-25 build/merge_popular_names.R

@@ -4,219 +4,78 @@ library(jsonlite)
 library(here)
 library(skimr)
 library(stringdist)
+library(here)
+#%% source helper functions
+
+source(here("build","match_two_laws.R"))
+
 
 #data 
-bdl_laws = read_csv(here("build","master.csv"))
-
-popnames_raw <- stream_in(file(here("build","popnames2.jsonl")))   %>%
-  tibble() %>%
-  filter(!cite_contains_title) %>%
-  mutate(raw_id=row_number()) 
-
-# ---- Popular Names
-
-# First we need to do some munging to work the data to the point where
-# each row is a single law
-
-# first problem, there are rows just cross-referencing other rows
-
-second_names = popnames_raw %>%
-  filter(!is.na(duplicate) & is.na(us_code)) %>% 
-  select(alternate_name=popular_name,popular_name=duplicate) %>%
-  group_by(popular_name) %>%
-  summarise(alternate_names=paste(alternate_name,collapse="|"),
-            number_of_alternate_names = n())
-
-# there is one strange act that has a citation and is a duplicate
-# but does not appear we can also add to avoid some issues later
-
-second_names = bind_rows(second_names,
-                         data.frame(popular_name="Randolph-Sheppard Act",
-                                    alternate_names="Randolph-Sheppard Vending Stand Act",
-                                    number_of_alternate_names=1))
+master = read_csv(here("build","master.csv"))
+popnames = read_csv(here('build',"popnames.csv")) %>%
+  select(-`...1`)
 
 
-# second issue, there are laws with the same public law number enacted on different dates!
-# we will simply drop these public laws because we don't have the time to address it
-suspicious_public_laws = popnames_raw %>%
-  group_by(public_law) %>%
-  summarise(number_of_unique_dates = length(unique(date)),
-            number_of_unique_citations=length(unique(citation))) %>%
-  filter(number_of_unique_dates>1 | number_of_unique_citations>1) %>%
-  filter(!is.na(public_law))
+master.vars = list(pl_no="pl_no",
+              congress_number="congress_number",
+              session="session_number",
+              chapter="chapter")
+
+popnames.vars = list(pl_no="pl_no",
+              congress_number="congress",
[…]

### 2023-09-25 build/pop_names_scrape.py

@@ -41,7 +41,8 @@ def pull_data(container):
     elif regex.match("\d+\\-\d+", law):
         out['public_law'] = law
     elif regex.match("\d{4},\s+ch\.\s+\d+",law):
-        out['year_and_chapter'] = law
+        year_and_chapter = law
+        out['chapter'] = regex.match("\d{4},\s+ch\.\s+(\d+)",law).group(1)
     else:
         raise ValueError("Unexpected law citation")
 
@@ -158,5 +159,5 @@ if __name__ == '__main__':
     for container in tqdm.tqdm(containers):
         df_raw.append(pull_data(container))
     df=pd.DataFrame(df_raw)
-    df.to_json(path_or_buf="build/popnames2.jsonl",orient='records',lines=True)
+    df.to_json(path_or_buf="build/popnames.jsonl",orient='records',lines=True)
     

### 2023-09-25 build/laws_and_subjects.py
updating toward finalization

@@ -1,0 +1,47 @@
+import scrapy
+from parsel import Selector 
+
+class LawsAndSubjectsSpider(scrapy.Spider):
+    name = 'laws_and_subjects'
+    allowed_domains = ['congress.gov']
+    
+    def clean_output(out):
+        for key in out:
+            if type(out[key]) == list:
+                out[key] = [i.strip() for i in out[key]]
+            else:
+                out[key] = out[key].strip()
+        return(out)
+    
+    def start_requests(self):
+        from requests import get
+        response = get("https://www.congress.gov/public-laws/93rd-congress")
+        root = Selector(response.text)
+        pls = root.xpath("//select[@id='congresses']/option/@value").extract()
+        for url in pls:
+            yield scrapy.Request(url='https://www.congress.gov'+url,callback=self.parse)
+        
+    def parse(self, response):
+        rows= response.xpath("""
+                        //table[contains(@class,'item_table')]/tbody/tr
+                        """)
+        for row in rows:
+            meta = {}
+            meta['public_law_number'] = row.xpath(
+                                'td[1]//text()').extract_first()
+            meta['bill_number'] = row.xpath("td[2]/a/text()").extract_first()
+            meta['bill_url'] = row.xpath("td[2]/a/@href").extract_first()
+            meta['bill_title'] =row.xpath('td[2]/text()').extract()
+            meta['date'] = row.xpath('td[3]/text()').extract_first()
+            url=meta['bill_url'] + '/subjects?overview=closed'
+            yield response.follow(url=url,
+                                 meta=meta,
+                                 callback=self.parse_bill_page)
+            
+    def parse_bill_page(self,response):
+        out = response.meta
+        out['policy_area'] = response.xpath(
+            "//div[@class='column-aside']/ul/li/a/text()").extract_first()
+        out['legislative_subjects'] = response.xpath(
+            "//div[@class='column-main']//li/a/text()").extract()
+        yield out

### 2023-09-25 build/nara.py

@@ -1,0 +1,88 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep 22 16:08:51 2023
+
+@author: brianlibgober
+"""
+
+from requests import get
+import re
+import pandas as pd
+from parsel import Selector
+from os.path import split,exists,join
+#%%
+def parse_block(block):    
+    block = block.strip()
+    elements = re.split("[\r\n]+",block)
+    bill_law = elements[0]
+    misc = elements[-1]
+    title = ' '.join(elements[1:-1])
+    bill, law = re.split("\s*/\s*",bill_law)
+    date,sal_citation,pages = re.split(";\s*",misc.strip("()"))
+    out = {}
+    out['bill'] =bill
+    out['public_law'] = law
+    out['date'] = date
+    out['sal_citation'] = sal_citation
+    out['pages'] = pages
+    out['title'] = title
+    return(out)
+
+
+
+
+def parse_summary(text,congress,session):
+    blocks = re.findall("[HS]\..*?(?=\n\s*\n|\Z)", text, re.DOTALL)
+    storage = []
+    for block in blocks:
+        parsed = parse_block(block)
+        parsed['congress'] =congress
+        parsed['session'] = 1 if session == 'first' else 2
+        storage.append(parsed)
+    return(storage)
+
+
+
+#%%
+template_url = 'https://www.archives.gov/files/federal-register/laws/{}-{}-session.txt'
+
+all_laws = []
+for congress in [115,116,117]:
+    for session in ['first','second']:
+        if (congress==117) and (session=='second'):
+            continue
+        url = template_url.format(congress,session)
+        _, path = split(url)
+        fpath = join("NARA",path)
+        if not exists(fpath):
+            response = get(url)
+            with open(fpath,"w+") as f:
+                f.write(response.text)
+        with open(fpath) as f:
+            text = f.read()
+        info = parse_summary(text,congress,session)  
+        all_laws =  all_laws + info
+        
+#%% now the more modern stuff
+url = 'https://www.archives.gov/federal-register/laws/117-second-session'
+response = get(url)
+s = Selector(response.text)
+rows = s.xpath("//table/tbody/tr")
+info = []
+for row in rows:
+    out = {}
+    out['bill'] = row.xpath("td[2]/text()").extract_first()
+    out['public_law'] = row.xpath("td[1]/text()").extract_first()
[…]

### 2023-09-25 make.sh

@@ -1,0 +1,32 @@
+
+# Build
+
+CWD=$(pwd)
+
+# make the heinonline files
+cd $CWD/build/heinonline/
+python main.py
+mv hein_data_raw.csv ..
+
+# gather the mods files
+cd $CWD/build
+Rscript gather_mods.R
+
+# combine the files
+
+Rscript combine_sources.R
+
+# build the popualr names data
+
+python pop_names_scrape2.py
+
+# merge prior collections
+
+Rscript merge_popular_names.R
+Rscript merge_sig_leg.R
+
+# evaluate merge quality/validation
+
+# compile latex
+
+

### 2023-09-25 draft/v1.tex
Updates from Overleaf

--- 2023-08-10 draft/v1.tex
@@
 \usepackage{lineno}
+\usepackage{subcaption}
 \linenumbers
 
-\title{A Comprehensive Dataset of U.S. Laws }
+\title{A Comprehensive Dataset of U.S. Federal Laws, 1789-2022}
 
@@
 \begin{abstract}
-Lists of US laws figure importantly in many research projects in political science, law, sociology, economics, and other disciplines.
-Yet despite their prominence and frequent use, there is no authoritative and complete dataset of all US laws.
-In part, this is because US laws have been enacted over hundreds of years, resulting in a complicated patchwork published in numerous and inconsistent formats.
-As a simplification, many scholars have relied upon more selective lists of \textit{major} legislative enactments, although the selection criteria for these narrower lists make their use questionable in many cases.
-Here, we describe our efforts to create a complete database of US laws and their revision histories by combining data from HEINOnline and Congress.gov.
+U.S.
+federal laws figure importantly in many research projects in political science, law, sociology, economics, and other disciplines.
+Despite their prominence, there is no authoritative, current, and comprehensive dataset of U.S.
+federal laws.
+In part, this is because such laws have been enacted over hundreds of years, resulting in a complicated patchwork of documents published in numerous and inconsistent formats.
+As a simplification, many scholars have relied upon more selective lists of \textit{major} legislative enactments, although the selection criteria for these narrower lists make their use questionable in many cases, or more comprehensive datasets of all laws, but only for specific time-periods.
+Here, I report on an effort to transparently and reproducibly assemble a complete database of US laws and their revision histories by combining data from HeinOnline, the Governmental Printing Office, and the National Archives and Records Administration.
+The result is a database of 49,746 laws spanning 1789 to 2022.
 \end{abstract}
@@
 
-In the US federal system, laws in the sense of ordinary usage can originate from many sources, including Courts, the President, agencies, and so forth.
-Yet when scholars speak more formally about the set of "US laws," they typically intend to refer to the set of authoritative documents enacted by the two chambers of the US Congress by following the legislative process.
-When Congress acts legislatively, it may do so by issuing a variety of documents that go by different names, have different formal features, and follow different processes.
-At present writing, the set of allowable actions include bills, joint resolutions, concurrent resolutions, and simple resolutions.
+What is a law?
+The Oxford English Dictionary defines it as "a rule or system of rules recognized by a country or community as regulating the actions of its members and enforced by the imposition of penalties." \cite{law2008} So defined, laws in the United States can originate from many sources, including courts, the President, executive agencies, and so forth, both at the state and the national-level.
+Yet when scholars speak more formally about the set of "U.S.
+laws," they often intend to refer to a smaller set of authoritative documents.
+In particular, they frequently mean those federal laws enacted by the two Congressional chambers, potentially over the President's veto, through the legislative process outlined in Article 1 Section 7 of the U.S.
+Constitution.
+When Congress acts legislatively in this fashion, it may do so by issuing a variety of documents that go by different names, have different formal features, and follow different internal processes.
+These can change and indeed have changed over time.
+At present writing, the set of allowable legislation include bills, joint resolutions, concurrent resolutions, and simple resolutions.
 Of these, only bills and joint resolutions have the general and binding character that one typically associates with laws.
-And even then, there are exceptions within these categories.
-``Private bills" granting relief in one-off cases\footnote{For example, last year Congress enacted a private law allowing Alaska-woman Rebecca Trimble to obtain permanent resident status, despite the fact the paperwork her adoptive parents had used to bring her to the United States from Mexico had been defective.} are typically not what scholars have in mind when one refers to ``laws'', nor are joint resolutions approving constitutional amendments which are not ratified by the states (e.g.
-the Equal Rights Amendment) really laws.
-That said, the set of enacted bills and joint resolutions is a relatively precise definition of what scholars \textit{should} mean when they talk about the set of US federal laws.
+And even then, there are exceptions and sub-divisions within these categories.
+``Private bills" granting relief in one-off cases\footnote{For example, last year Congress enacted a private law allowing Alaska-woman Rebecca Trimble to obtain permanent resident status, despite the fact the paperwork her adoptive parents had used to bring her to the United States from Mexico had been defective.} are typically not what scholars have in mind when one refers to ``laws.'' Nor are joint resolutions approving constitutional amendments which are not ratified by the states really laws (e.g.
+the Equal Rights Amendment) .
+That said, the set of enacted bills and joint resolutions is a relatively precise definition of what scholars \textit{should} mean when they talk about the set of U.S.
+federal laws.
+Surprisingly, there is not, at least to the authors knowledge a transparent, fully comprehensive, and almost current database of these documents.
 
-Studies of lawmaking in US political science are not new.
-Indeed, a very important debate in political science over the past several decades has to do with whether unified government, where the President and Congress are controlled by the same party, is better or worse for legislative productivity than divided government, where these organs are not exclusively in controlled by the same political party.
-This debate was initiated by Mayhew (1991) \nocite{Mayhew1991}, who published a list of ``major'' legislative enactments identified by the set of laws that were mentioned in the editorial page of the New York Times and other prominent newspapers.
-This list of major enactments has been updated annually since its original publication in 1991 and is, at present writing, current from 1947 through 2022.
-Of course, the coverage of major legislative enactments is obviously limited as a database of all federal laws, both because it does not cover laws that fail to draw the attention of editorial pages, nor does it cover laws enacted during the New Deal or earlier.
+While this lack of data is surprising given the importance of US federal lawmaking to so many areas of social scientific inquiry, there obviously have been numerous important efforts that come close.
+Probably the closest data that exists emerges from a key debate in American political science over the past several decades about the consequences of divided government.
+In particular, scholars have wondered whether the state of unified government, where the President and Congress are controlled by the same party, is better or worse for legislative productivity than divided government, where these organs are not exclusively in controlled by the same political party.
+This debate was initiated by Mayhew (1991) \nocite{Mayhew1991}, who engaged this question quantitatively through a dataset of ``major'' legislative enactments.
+With slight simplification, Mayhew identified those pieces of legislation that were substantial through analyzing newspaper articles that summarized the achievements of the past legislative session, as we well as an examination of specialized historical works that retrospectively evaluated the importance of key pieces of legislation in a large number of policy areas.
+Mayhew's list of major enactments has been updated annually since its original publication in 1991 and is, at present writing, current from 1947 through 2022.
+Of course, this coverage of major legislative enactments is obviously limited as a database of all federal laws, both because it does not cover laws that fail to draw the attention of editorial pages, nor does it cover laws enacted during the New Deal or earlier.
+Three issues implicit in Mayhew's pathbreaking data collection and analysis have continued to bedevil social scientists working in this area: transparency and reproducibility of inclusion or exclusion criteria, limited temporal coverage, and comprehensiveness within covered time-periods.
 
-Addressing these weaknesses has been the subject of at least two other major research projects.
-The Policy Agendas Project is a long-standing collaborative research effort aimed at building multiple datasets for tracking and comparing which issues manage to attract the attention of government across.
-It covers many national and subnatnional systems, including hte United States federal government.
-In particular, their database of bills covers "more than 400,000 bills introduced by the US Congress." Importantly, they also have coded each bill according to the subject-matter coding system of the larger Policy Agenda Project.
+ There have been several follow-up efforts to Mayhew's project that are notable for their attempt to extend data on legislative enactments in various ways.
+Howell et al (2000) collect data on 17,633 public laws enacted between 1945 and 1994 and categorize them into four bins of importance, finding critical differences in terms of legislative productivity across unified and divided government according to legislative significance.
+\cite{Howell2000} Clinton and Lapinski (2006) enter the same debate by introducing an IRT model for estimating the importance of enacted laws between 1877 and 1994,\cite{clinton2006measuring} and have subsequently used these same data and estimates to reconsider questions about the interpretation of roll-call votes as a measure of political ideology \cite{clinton2008laws,lapinski2008,bateman2017}.
+The Clinton-Lapinski model of legislative importance leverages an even more comprehensive assembly than the Howell et al effort, comprising some 37,766 law going all the way back to the post-Civil War era.\footnote{At present writing this database was avialable at one of the author's websites, \url{https://my.vanderbilt.edu/joshclinton/data/}} Yet to the authors knowledge, this comprehensive dataset has not been updated to include laws enacted in the last two decades.
+Nor does it extend backwards into the first century of the US Republic.
+
+Several other major research projects partially address the issue of currency and comprehensiveness, but neither in a completely satisfactory way.
+The Policy Agendas Project, for example, is a long-standing collaborative research effort aimed at building multiple datasets for tracking and comparing which issues manage to attract the attention of government across.
+It covers many national and subnational systems, including the United States federal government.
+In particular, their database of bills covers "more than 400,000 bills introduced by the U.S.
+Congress." Importantly, they also have coded each bill according to the subject-matter coding system of the larger Policy Agenda Project.
 Their focus on covering the subject matter of lawmaking is an important undertaking, although arduous, and it is unsurprising given the difficulties of this undertaking that they have only managed to cover the period 1947-2022.
-The second project with relevant and similar prior data collection is due to Ansolabehere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016,ansolabehere2018divided} Their data collection, which was conducted under the auspices of an undergraduate course at Harvard called ``"What Has Congress Done," crowd-sourced the task of identifying significant legislation to students, each of whom was responsible for producing a list of significant legislation enacted under each of 22 potentially assigned decades.
+The second project with relevant and similar prior data collection is due to Ansolabehere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016,ansolabehere2018divided} Their data collection, which was conducted under the auspices of an undergraduate course at Harvard called ``What Has Congress Done," crowd-sourced the task of identifying significant legislation to students, each of whom was responsible for producing a list of significant legislation enacted under each of 22 potentially assigned decades.
 The researchers provided a list of secondary sources, as well as guidance and quality control efforts.
 Similar to Mayhew, their criteria for inclusion were (a) was the law considered significant at the time of enactment, and (b) does the law seem significant in historical perspective.
-Because of their differing methods, the two sources do not completely overlap in the 1947-2022 period.
-Although the temporal coverage for the Ansolabehere, Palmer, and Schneer dataset is very comprehensive, it contains a small percentage of all laws enacted by the US Congress.
+Because of their differing methods, Mayhew and Ansolabhere, Palmer and Schneer do not completely overlap in the 1947-2022 period as databases of significant legislation.
+Although the temporal coverage for the Ansolabehere, Palmer, and Schneer dataset is very comprehensive, it contains a small percentage of all laws enacted by the U.S.
+Congress.
+None of the so-far mentioned sources, therefore, comes anywhere near a comprehensive dataset of US laws.
 
-% A few OTHER PAPERS
-% Clinton and Lapinski (2006)
-% Stathis (2014)
-% Howell, William, Scott Adler, Charles Cameron, and Charles Riemann (2000) “Divided government
-and the legislative productivity of Congress, %1945–94.” Legislative Studies Quarterly 25 (2): 285–
-%312
-
-There are several reasons why it is desirable to have a more complete dataset of US lawmaking than has previously existed.
-In particular, minor legislation is usually major to somebody, otherwise they would not go through the trouble of passing it.
+%There are several reasons why it is desirable to have a more complete dataset of U.S.
+lawmaking than has previously existed.
+Temporarlly In particular, minor legislation is usually major to somebody, otherwise why would someone go to the trouble of passing it?
 While focusing on the big pieces of legislation is perhaps appropriate for thinking about how party control effects the ability of collective government to solve the big problems, a more granular perspective is really necessary to think about how special interests may whittle away the gains made by broad coalitions through smaller pieces of legislation, or perhaps how policy fails to make the necessary incremental adjustments to keep with the times.
 There is notable inconsistency in what laws are included as significant using all these methods.
-The lack of a unified and complete dataset also frustrates progress of the discipline, as these authors do not necessarily use the same system to refer to particular laws, making US law datasets used by social scientist less inter-operable than they should be.
+The lack of a unified and complete dataset also frustrates progress of the discipline, as these authors do not necessarily use the same system to refer to particular laws, making U.S.
+law datasets used by social scientist far less inter-operable than they should be.
+The lack of inter-operability frustrates project
 
-Our project seeks to build a comprehensive and easily updated list of US laws and their revision histories based on publicly available sources.
-The two key sources we leverage are the Statutes at Large, for laws existing before 2012, and Congress.gov, for more recent laws.
-The Congress.gov component is downloadable by webscraping and is relatively uncomplicated.
-The more challenging part of the project involves cataloguing the older set of laws contained within the Statutes at Large.
-Surprisingly, the US government does not make electronic copies of the Statutes at Large available prior to 1951,\footnote{https://www.govinfo.gov/app/collection/statute/2016}, despite the fact that there were 64 earlier volumes containing laws that in many cases have not been amended.
-Despite the surprising limited availability of these foundational documents, a database widely used by legal scholars, HeinOnline, has digitized all these books in their entirety and provided meta data on their table of contents.
-Laws are identified in the statutes of laws in various and not perfectly ways across the decades.
-For this reason, we supply a more consistent set of identifiers that, going forward, allows laws to be easily matched by researchers.
-We describe these identifiers in more detail in the usage section below.
-Additionally, we include a set of text data that corresponds to these laws, although particularly for earlier laws these are collected via OCR.
+This project seeks to build a comprehensive and easily updated list of U.S.
+laws and their revision histories based on publicly available sources.
+The primary source we leverage is the Statutes-at-Large, which has been published continuously since 1845, and whose early issues contain the earliest legislative enactments.
+The most recent issue of the Statutes-at-large is from 2017, and it is published with about a six year delay.
+Even though the statutes at large are not physically or electronically available for the last six years, the National Archives and Records Administration provides citations to page numbers almost immediately.\footnote{For example, on September 25, 2023 it was possible to get the statute at large citation of a law enacted only three days prior \url{https://web.archive.org/web/20230925173228/https://www.archives.gov/federal-register/laws/current.html}}
+
+Although the Statutes at Large are well-known to scholars, this source have not until recently been ``born digital." As a result, when electronic data on these laws are available, they have typical issues of digitized text data, despite the very high importance of these documents.
+Indeed, it is somewhat surprising that the U.S.
+government does not make electronic copies of the Statutes at Large available prior to 1951,\footnote{https://www.govinfo.gov/app/collection/statute/2016} despite the fact that there were 64 earlier volumes containing laws that in many cases have not been amended.
+In legal practice, not having these documents digitized usually works out well enough, because of ongoing public and private efforts to develop codices of laws, however there are occasional issues of interpretation where returning to the actual text of the law in the Statutes-at-Large is necessary.
+In addressing such esoteric issues, legal scholars and lawyers often leverage use an electronic database called HeinOnline, which has digitized all these paper volumes in their entirety.
+Fortunately, they also provide meta data on the tables of contents of these volumes.
+For years in which the government-provides meta-data about laws through its Governmental Printing Office, we can rely on this meta-data to construct a list of laws.
+For older years that the GPO has not yet reached, we rely on the meta-data provided by HeinOnline.
+For more recent years where the Statutes at Large do not yet exist, we rely on data on the National Archives website to supplement and bring our dataset to currency.\footnote{https://www.archives.gov/federal-register/laws.
+Per that site, ``After the President signs a bill into law, it is delivered to the Office of the Federal Register (OFR)[, a division of the National Archives], where editors: assign a Public Law Number[,] prepare it for publication as a Slip Law[,] include it in the next edition of the United States Statutes at Large.''}
+
+ Our dataset covers laws enacted from 1789 to 2022, the year prior to publication, and contains 49,746 entries.
+A Github repository provides linked to this publication provides code to update the set of laws to the present.
 
@@
 
-We rely on two primary sources for our comprehensive database of US laws: the U.S. Statutes at Large, as disseminated via HeinOnline, and Congress.gov.
+We rely on three primary sources for our comprehensive database of U.S.
+laws: the oldest meta data for the U.S.
+Statutes at Large disseminated via HeinOnline, similar and more recent meta data through the Governmental Printing Office, and finally the last six years of law-making as described by the National Archives' website.
 
-For our data collection based on HeinOnline, we began by scraping the table of contents of each volume of the statues at large, excepting volumes 6-8 which contain a collection of early treaties and private laws.
-Examination of these tables reveals that laws are identified using various citation systems depending on era.
+We began our data collection by scraping the table of contents of each volume of the Statues at Large, excepting volumes 6-8 which contain a collection of early treaties and private laws.
+Importantly, examination of these tables of contents quickly reveal weaknesses in many approaches to uniquely identifying laws.
+In particular, the public law numbers used today were not used consistently prior to the 20th century.
+There were also periods in the 20th century where public law numbers were repeated across sessions of the same convening of Congress, as opposed to more recent practice where the new session of a particular Congress starts counting where it left off in the last session.
+Citing pages and volumes of the Statutes-at-Large, probably the most common practice in ordinary government and legal use, does not effectively disambiguate laws because it is not uncommon for two or even three laws to share the same starting page.
+Presumably, individuals who care about the text of a particular law know how to fill in the gaps caused by this ambiguity, however for the purposes of building \textit{databases} this is clearly not ideal.
+Disambiguating based on the names of the laws is possible, but potentially mistake prone as different sources may use different capitalizations, punctuation, and spacing, short versus long names, and other issues typical of text data.
+
+These caveats aside, examination of the published pages of the statutes at large as well as the table of contents reveals that laws \textit{are} identified using (almost perfectly) precise numerical citation systems, however the exact system that works depends on the era.
 In particular,
@@
 \begin{itemize}
-\item The currently practiced identification system begins on Jan 7, 1959 with the 86th Congress.
+\item The currently practiced identification system ("Late regime") begins on Jan 7, 1959 with the 86th Congress.
 In this system, laws are identified by the number of the Congress and the law number within Congress.
-An example is ``Public Law 105-89, An Act: to promote the adoption of children in foster care.''
-\item Initially, laws were identified by a different system.
+An example is ``Public Law 105-89, An Act: to promote the adoption of children in foster care.'' There is only one Public Law 105-89, it uniquely refers to that titled law, and the statutes-at-large has published the text of the law with that identifier.
+\item Initially, laws were identified by a different system ("Early Regime").
 From the 1st through the 56th Congress, which concluded March 3, 1901, laws were identified in the Statutes at Large by chapter as well as Congress and session (e.g.
-``Chapter 15, 56 Congress, Session 1, An Act: Relating to Cuban vessels.")
-\item For the 57th through 85th congress, the Statutes at Large inconsistently use both systems, with the important caveat that chapters and public laws are sometimes recycled over the two sessions of a particular Congress.\footnote{Or worse, the same session.
-Indeed, PL 65-246 refers to both a law ``Providing for the transportation from the District of Columbia of governmental employees whose services no longer are required." and also a law intended ``To authorize the sale of certain lands to school district numbered twenty-eight, of Missoula County, Montana."} Careful attention to chapters, public laws, and sessions does disambiguate all laws, however these details are very particular and subtle.
+``Chapter 15, 56 Congress, Session 1, An Act: Relating to Cuban vessels.").
+All laws in the statutes-at-large are published with this information during the early period.
+The Early Regime and Later Regime are not interoperable, as the published pages of the statutes at large in the early period do not provide public law numbers and the published pages in later period do not provide chapters.
+\item For the 57th through 85th congress, the Statutes at Large uses both systems, but not always consistently.
+Indeed, a key difficulty in this period is that chapters and public laws are sometimes recycled within one Congress over multiple sessions of a particular Congress.\footnote{And worse, in just a few instances, the same session.
+Indeed, PL 65-246 refers to both a law ``Providing for the transportation from the District of Columbia of governmental employees whose services no longer are required." and also a law intended ``To authorize the sale of certain lands to school district numbered twenty-eight, of Missoula County, Montana."} Careful attention to chapters, public laws, and sessions does disambiguate nearly all laws, however these details are very particular and subtle.
 \end{itemize}
 
-Following these citation practices, we used a rule-based parser to extract key pieces of information to identify the law.
+ Following these citation practices, we used a rule-based parser to extract key pieces of information from scraped meta-data to build a database of laws.
 Technical validation efforts revealed that there were occasional errors of transcription in our source data, for example mis-identification of chapters associated with laws or including page numbers that were not correct.
@@
 
+The primary dataset we provide is publicly available at https://osf.io/qa289. Additionally, a Github repository that was used to construct the dataset will be made available upon publication.
+
 % The Data Records section should be used to explain each data record associated with this work, including the repository where this information is stored, and to provide an overview of the data files and their formats.
@@
 We offer two primary approaches to support the technical validation of our dataset.
-The first is to compare the total counts of laws by Congress against previously published totals while the second validation exercise is to show that all of the laws described in five distinct sources of major laws are, indeed, present in our dataset.
+The first is to compare the total counts of laws by Congress against total counts previously published by social scientists.
+The second validation exercise involves showing that we cover well a particularly comprehensive dataset of laws published by the Office of Revision Counsel, the agency within Congress  responsible for preparing the U.S.
+Code.
 
-The reference counts for total laws that we rely on comes from Appendix F reported in Galloway and Wise's History of the House of Representatives, and also previously used for validation and analysis by Ansolabhere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016} Our definition of law is slightly more capacious than theirs, in the sense that we also consider "Joint Resolutions" laws, and the authors admit their own counts combine acts and resolutions (the latter of which are not, in our view, best understood as laws) from the 77th Congress and after.
+The reference counts for total laws that we rely on comes from Appendix F reported in Galloway and Wise's History of the House of Representatives\nocite{gallowaywise}.
+It was the same set of reference counts previously used for validation and analysis by Ansolabhere, Palmer, and Schneer\cite{ansolabehere_palmer_schneer_2016}.
+Our definition of law is slightly more capacious than Galloway and Wise's, in the sense that we also consider "Joint Resolutions" laws, and the authors admit their own counts combine acts and resolutions (the latter of which are not, in our view, best understood as laws) from the 77th Congress and after.
+Nevertheless, it is possible to subset our data in such a way as to include the same set of documents as Galloway and Wise cover, and thereby constitute an appropriate test of technical validity.
 Figure \ref{fig:totals} compares the counts for this key subset of our data.
-Note that the total deviation in counts is X.
-An undergraduate research assistant further investigated the difference in counts of laws in Congress A and B.
-In both cases, the number of laws that the research assistant counted in that Congress was the same as the number we provided.
+Note that in total Galloway and Wise count 23,155 laws, while we would peg the figure at 23,152, or three laws fewer ($\approx 0.13\%$ of the total).
+The true discrepancy between our counts and Appendix F is somewhat greater, because in some years our counts are higher than Galloway \& Wise's and in some years lower.
+However, in all but six Congresses, our counts are identical.
+Summing up the absolute value of the difference in counts in these six Congresses, we arrive at a total difference in counts of 11, again a very small difference on a percentage basis.
+An undergraduate research assistant further investigated the difference in counts of laws in  the 11th, 15th, and 34th Congress.
+In each case, the number of laws that the research assistant counted in that Congress was the same as the number we provided, and we were unable to determine why there was a discrepancy between the Galloway and Wise total and our own.
 
-A second 
-\
+Our second validation exercise works by attempting to match our database of laws against a particularly large collection of U.S.
+laws.
+The dataset we use is the table of official popular names for Congressional enactments as produced by the Office of Revision Counsel.\footnote{https://uscode.house.gov/popularnames/popularnames.htm} This table catalogues in its rows a set of 13,170 popular or short-names for official legal acts.
+The table's rows have entries such as ``Obamacare," which directs readers to see another row on the ``Patient Protection and Affordable Care Act." In the row corresponding to the ``Patient Protection and Affordable Care Act," the table provide a citation ``Pub.
+L.
+111-148, Mar.
+23, 2010,124 Stat.
+119." Although the table contains many hundreds of rows cross-referencing entries, which are not directly useful for testing, the source nevertheless can be used to construct a very strong validation test of our source data.
+In particular, it has very long temporal coverage, especially as compared with most datasets of important legislation, and it has very deep coverage, as it cites many thousands more laws than most other datasets.
+The main alternative contender with equivalent temporal coverage, the crowd-sourced dataset produced by Ansolabhere, Palmer, and Schneer,\cite{ansolabehere_palmer_schneer_2016} has many thousands less laws and follows considerably less consistent citation practices than the Office of Revision Counsel.
+
+That said, while the Popular Names Table is a very good source for validating, there are a few difficulties.
+First, and perhaps most importantly, the popular names table includes names for specific \textit{pieces} of legislation that are part of larger legislative enactments.
+For example, the Biggert-Waters Flood Insurance Reform Act of 2012 refers just to subtitle A of Title II of Division F of a 584-page highway bill enacted in the same year (Public Law  112-141).
+While our database of laws does include 112-141 as a law, it does not include titles and sub-titles like the Biggert-Waters Act, so such rows need to be excluded from our matching exercise.
+Secondly, even after screening out these subpart the popular names table also includes a number of suspicious entries.
+These involve issues such as two names referring to the same public law number but claiming different enactment dates.
+This issue impacts some 745 entries, which is a considerable number, and there are also other similarly suspicious issues involving citations.
+Because of these and several other issues, and also because the number of laws with popular names is considerably smaller than the number of laws, we view the key test of our dataset as what proportion of the \textit{unproblematic entries} in the popular names table are matchable against our complete enumeration of U.S.
+laws.
+We find that out of 7,315 cleanly cited laws in the popular names table, we are able to match 7,229 to our list of U.S.
+laws (98.8\%).
+Part of the reason we are not able to do even better is that the popular names table does not always disambiguate page citations to the statute at large by referring to chapter or other suitable citation.
+As a result, if there are multiple laws on a particular page we cannot automatically tell which popular name goes with which law on that page.
+If we count those popular names matching to more than one law as a ``hit" in our query, it turns out we find 7,284 matches, which is to say 99.6\% of all the laws we search for can be found in our database.
 
 \section*{Usage Notes}  \label{sec:usage}
+
+While we provide a numeric identifier that can be used for referring to particular rows of our dataset, we recommend that future researchers use identification for laws that reflect greater attention to the inconsistencies in citation practice over time.
+In particular,  we recommend matching efforts that use piece-wise rules as outlined in the methods section above and implemented via special merging functions in the git repository.
+Beginning with the 86th Congress laws should be matched using the public law number.
+Prior to the 56th Congress, laws should be matched by chapter number, Congress, and session.
+Finally, particular care needs to be paid in the matching of laws enacted between the 57th and 85th Congress.
+Generally, if public laws and chapters will be used to refer to laws in a dataset that is not exclusively relating to recent laws, one \textit{must} also include the Congressional session (or equivalently include the date of enactment, from which one can infer these details).
 
@@
 \section*{Code availability}
+
+All code used to create the dataset from original sources, is available through a Github repository made public upon publication.
+Also included in the repository are code and data used to validate the dataset as well as generate the figure.
+\footnote{\url{https://github.com/libgober/database_of_laws}}
 
@@
 \section*{Figures \& Tables}
+
+\begin{figure}[h]
+  \centering
+  \caption{Number of Acts of Congress by Meeting of Congress.}
+  \includegraphics[width=\linewidth]{draft/figures/counts_of_laws.png}
+    \label{fig:totals}
+\end{figure}
 

### 2023-09-27 build/combine_sources.R
final submission fixes

@@ -1,5 +1,7 @@
 library(tidyverse)
 library(here)
+library(jsonlite)
+library(lubridate)
 
 Mods = read_csv(here("build","mods.csv")) %>%
   mutate(Source="GPO")

### 2023-09-27 build/mods/merge_sigleg.R

@@ -1,154 +1,0 @@
-
-#libraries
-library(readxl)
-library(dplyr)
-library(tidyverse)
-library(tidyr)
-library(jsonlite)
-library(stringr)
-library(here)
-library(assertthat)
-
-#load data
-
-raw_data = read_csv(here('build','significant_legislation_database.csv'))
-corrections = read_csv(here("build","aps_corrections.csv"))
-
-master = read_csv(here('build','master.csv'))
-
-# cleaning raw data from replication file and other fixes
-
-APS_fixed = bind_rows(raw_data %>%
-  anti_join(corrections,by="id"),
-  corrections) %>%
-  filter(category!='Constitutional Amendment')
-
-#note that there are a few non laws
-dropids = c(1224)
-
-APS_fixed=APS_fixed %>%
-  filter(!(id %in% dropids))
-            
-            
-          
-
-
-APS_fixed$pl <- gsub("PL", "", APS_fixed$pl)
-APS_fixed$pl <- gsub(" ", "", APS_fixed$pl)
-APS_fixed$pl <- gsub("N/A", "", APS_fixed$pl)
-APS_fixed$pl <- gsub("Failed", "", APS_fixed$pl)
-APS_fixed$pl <- gsub("NONE", "", APS_fixed$pl)
-APS_fixed$pl <- gsub("_", "-", APS_fixed$pl)
-
-
-stat_at_large_regex = "(\\d+)\\s*Stat\\.?\\s*(\\d+)"
-
-stat_large_citations1= APS_fixed %>%
-  filter(!is.na(pl) & nchar(pl)>1) %>%
-  select(id,pl) %>%
-  mutate(
-    sal_volume=str_extract(pl,stat_at_large_regex,group=1),
-         sal_page_start=str_extract(pl,stat_at_large_regex,group=2)) %>%
-  select(-pl) %>%
-  filter(!is.na(sal_volume) & !is.na(sal_page_start))
-  
-stat_large_citations2 = APS_fixed %>%
-  filter(!(str_detect(pl,stat_at_large_regex) )) %>%
-  select(id,legislation) %>%
-  mutate(
-    sal_volume=str_extract(legislation,stat_at_large_regex,group=1),
-    sal_page_start=str_extract(legislation,stat_at_large_regex,group=2))  %>%
-  select(-legislation) %>%
-  filter(!is.na(sal_volume) & !is.na(sal_page_start))
-
-#check that these don't overlap
-intersect(stat_large_citations1$id,stat_large_citations2$id)
-
[…]

### 2023-09-27 draft/v1.tex

@@
 In part, this is because such laws have been enacted over hundreds of years, resulting in a complicated patchwork of documents published in numerous and inconsistent formats.
-As a simplification, many scholars have relied upon more selective lists of \textit{major} legislative enactments, although the selection criteria for these narrower lists make their use questionable in many cases, or more comprehensive datasets of all laws, but only for specific time-periods.
+As a simplification, many scholars have relied upon selective lists of major legislative enactments or complete lists of relatively recent enactments.
 Here, I report on an effort to transparently and reproducibly assemble a complete database of US laws and their revision histories by combining data from HeinOnline, the Governmental Printing Office, and the National Archives and Records Administration.
@@
 When Congress acts legislatively in this fashion, it may do so by issuing a variety of documents that go by different names, have different formal features, and follow different internal processes.
-These can change and indeed have changed over time.
+These sub-genre distinctions can and indeed have changed over time.
 At present writing, the set of allowable legislation include bills, joint resolutions, concurrent resolutions, and simple resolutions.
@@
 ``Private bills" granting relief in one-off cases\footnote{For example, last year Congress enacted a private law allowing Alaska-woman Rebecca Trimble to obtain permanent resident status, despite the fact the paperwork her adoptive parents had used to bring her to the United States from Mexico had been defective.} are typically not what scholars have in mind when one refers to ``laws.'' Nor are joint resolutions approving constitutional amendments which are not ratified by the states really laws (e.g.
-the Equal Rights Amendment) .
-That said, the set of enacted bills and joint resolutions is a relatively precise definition of what scholars \textit{should} mean when they talk about the set of U.S.
-federal laws.
+the Equal Rights Amendment).
+Despite this esoteric mess of terminology, the set of enacted bills and joint resolutions is a relatively precise definition of what scholars \textit{should} mean when they talk about the set of U.S.
+federal laws, that is to say federal legislative enactments with a binding public character.
 Surprisingly, there is not, at least to the authors knowledge a transparent, fully comprehensive, and almost current database of these documents.
 
-While this lack of data is surprising given the importance of US federal lawmaking to so many areas of social scientific inquiry, there obviously have been numerous important efforts that come close.
-Probably the closest data that exists emerges from a key debate in American political science over the past several decades about the consequences of divided government.
+ Given the importance of U.S.
+federal lawmaking, it is surprising that no data source meets these goals of coverage and transparency.
+Yet it is worth detailing the numerous and painstaking data collection efforts that have come increasingly close.
+Some of the earliest existing data responsive to these criteria comes from a key debate in American political science about the consequences of divided government.
 In particular, scholars have wondered whether the state of unified government, where the President and Congress are controlled by the same party, is better or worse for legislative productivity than divided government, where these organs are not exclusively in controlled by the same political party.
@@
 The Clinton-Lapinski model of legislative importance leverages an even more comprehensive assembly than the Howell et al effort, comprising some 37,766 law going all the way back to the post-Civil War era.\footnote{At present writing this database was avialable at one of the author's websites, \url{https://my.vanderbilt.edu/joshclinton/data/}} Yet to the authors knowledge, this comprehensive dataset has not been updated to include laws enacted in the last two decades.
-Nor does it extend backwards into the first century of the US Republic.
+Nor does it extend backwards into the first century of the U.S.
+Republic.
+As we shall see, that leaves about 25\% of all laws and almost 100 years of law-making uncovered.
 
 Several other major research projects partially address the issue of currency and comprehensiveness, but neither in a completely satisfactory way.
+It is also worth emphasizing that these projects all use somewhat different approaches to identifying laws, which are mostly but not perfectly inter-operable.
 The Policy Agendas Project, for example, is a long-standing collaborative research effort aimed at building multiple datasets for tracking and comparing which issues manage to attract the attention of government across.
@@
 Their focus on covering the subject matter of lawmaking is an important undertaking, although arduous, and it is unsurprising given the difficulties of this undertaking that they have only managed to cover the period 1947-2022.
-The second project with relevant and similar prior data collection is due to Ansolabehere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016,ansolabehere2018divided} Their data collection, which was conducted under the auspices of an undergraduate course at Harvard called ``What Has Congress Done," crowd-sourced the task of identifying significant legislation to students, each of whom was responsible for producing a list of significant legislation enacted under each of 22 potentially assigned decades.
+
+Another project with relevant and similar prior data collection is due to Ansolabehere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016,ansolabehere2018divided} Their data collection, which was conducted under the auspices of an undergraduate course at Harvard called ``What Has Congress Done," crowd-sourced the task of identifying significant legislation to students, each of whom was responsible for producing a list of significant legislation enacted under each of 22 potentially assigned decades.
 The researchers provided a list of secondary sources, as well as guidance and quality control efforts.
@@
 Because of their differing methods, Mayhew and Ansolabhere, Palmer and Schneer do not completely overlap in the 1947-2022 period as databases of significant legislation.
-Although the temporal coverage for the Ansolabehere, Palmer, and Schneer dataset is very comprehensive, it contains a small percentage of all laws enacted by the U.S.
+Although the temporal coverage for the Ansolabehere, Palmer, and Schneer dataset is very long, it contains a small percentage of all laws enacted by the U.S.
 Congress.
-None of the so-far mentioned sources, therefore, comes anywhere near a comprehensive dataset of US laws.
+None of the so-far mentioned sources, therefore, comes anywhere near a comprehensive dataset of U.S.
+laws.
 
@@
 laws and their revision histories based on publicly available sources.
-The primary source we leverage is the Statutes-at-Large, which has been published continuously since 1845, and whose early issues contain the earliest legislative enactments.
-The most recent issue of the Statutes-at-large is from 2017, and it is published with about a six year delay.
-Even though the statutes at large are not physically or electronically available for the last six years, the National Archives and Records Administration provides citations to page numbers almost immediately.\footnote{For example, on September 25, 2023 it was possible to get the statute at large citation of a law enacted only three days prior \url{https://web.archive.org/web/20230925173228/https://www.archives.gov/federal-register/laws/current.html}}
+The primary source we leverage is the \emph{Statutes at Large}, which has been published continuously since 1845, and whose early issues contain the earliest legislative enactments.
+The most recent issue of the \emph{Statutes at Large} is from 2017, and it is published with about a six year delay.
+Even though the \emph{Statutes at Large} are not physically or electronically available for the last six years, the National Archives and Records Administration provides citations to page numbers almost immediately.\footnote{For example, on September 25, 2023 it was possible to get the statute at large citation of a law enacted only three days prior \url{https://web.archive.org/web/20230925173228/https://www.archives.gov/federal-register/laws/current.html}}
 
-Although the Statutes at Large are well-known to scholars, this source have not until recently been ``born digital." As a result, when electronic data on these laws are available, they have typical issues of digitized text data, despite the very high importance of these documents.
+Although the \emph{Statutes at Large} are well-known to scholars, this source have not until recently been ``born digital." As a result, when electronic data on these laws are available, they have typical issues of digitized text data, despite the very high importance of these documents.
 Indeed, it is somewhat surprising that the U.S.
-government does not make electronic copies of the Statutes at Large available prior to 1951,\footnote{https://www.govinfo.gov/app/collection/statute/2016} despite the fact that there were 64 earlier volumes containing laws that in many cases have not been amended.
-In legal practice, not having these documents digitized usually works out well enough, because of ongoing public and private efforts to develop codices of laws, however there are occasional issues of interpretation where returning to the actual text of the law in the Statutes-at-Large is necessary.
+government does not make electronic copies of the \emph{Statutes at Large} available prior to 1951,\footnote{https://www.govinfo.gov/app/collection/statute/2016} despite the fact that there were 64 earlier volumes containing laws that in many cases have not been amended.
+In legal practice, not having these documents digitized usually works out well enough, because of ongoing public and private efforts to develop codices of laws, however there are occasional issues of interpretation where returning to the actual text of the law in the \emph{Statutes at Large} is necessary.
 In addressing such esoteric issues, legal scholars and lawyers often leverage use an electronic database called HeinOnline, which has digitized all these paper volumes in their entirety.
@@
 For older years that the GPO has not yet reached, we rely on the meta-data provided by HeinOnline.
-For more recent years where the Statutes at Large do not yet exist, we rely on data on the National Archives website to supplement and bring our dataset to currency.\footnote{https://www.archives.gov/federal-register/laws.
-Per that site, ``After the President signs a bill into law, it is delivered to the Office of the Federal Register (OFR)[, a division of the National Archives], where editors: assign a Public Law Number[,] prepare it for publication as a Slip Law[,] include it in the next edition of the United States Statutes at Large.''}
+For more recent years where the \emph{Statutes at Large} do not yet exist, we rely on data on the National Archives website to supplement and bring our dataset to currency.\footnote{https://www.archives.gov/federal-register/laws.
+Per that site, ``After the President signs a bill into law, it is delivered to the Office of the Federal Register (OFR)[, a division of the National Archives], where editors: assign a Public Law Number[,] prepare it for publication as a Slip Law[,] include it in the next edition of the United States \emph{Statutes at Large}.''}
 
@@
 laws: the oldest meta data for the U.S.
-Statutes at Large disseminated via HeinOnline, similar and more recent meta data through the Governmental Printing Office, and finally the last six years of law-making as described by the National Archives' website.
+\emph{Statutes at Large} disseminated via HeinOnline, similar and more recent meta data through the Governmental Printing Office, and finally the last six years of law-making as described by the National Archives' website.
 
-We began our data collection by scraping the table of contents of each volume of the Statues at Large, excepting volumes 6-8 which contain a collection of early treaties and private laws.
+We began our data collection by scraping the table of contents of each volume of the \emph{Statutes at Large}, excepting volumes 6-8 which contain a collection of early treaties and private laws.
 Importantly, examination of these tables of contents quickly reveal weaknesses in many approaches to uniquely identifying laws.
@@
 There were also periods in the 20th century where public law numbers were repeated across sessions of the same convening of Congress, as opposed to more recent practice where the new session of a particular Congress starts counting where it left off in the last session.
-Citing pages and volumes of the Statutes-at-Large, probably the most common practice in ordinary government and legal use, does not effectively disambiguate laws because it is not uncommon for two or even three laws to share the same starting page.
+Citing pages and volumes of the \emph{Statutes at Large}, probably the most common practice in ordinary government and legal use, does not effectively disambiguate laws because it is not uncommon for two or even three laws to share the same starting page.
 Presumably, individuals who care about the text of a particular law know how to fill in the gaps caused by this ambiguity, however for the purposes of building \textit{databases} this is clearly not ideal.
@@
 
-These caveats aside, examination of the published pages of the statutes at large as well as the table of contents reveals that laws \textit{are} identified using (almost perfectly) precise numerical citation systems, however the exact system that works depends on the era.
+These caveats aside, examination of the published pages of the \emph{Statutes at Large} as well as the table of contents reveals that laws \textit{are} identified using an (almost perfectly) precise numerical citation systems, however the exact system that works depends on the era.
 In particular,
@@
 In this system, laws are identified by the number of the Congress and the law number within Congress.
-An example is ``Public Law 105-89, An Act: to promote the adoption of children in foster care.'' There is only one Public Law 105-89, it uniquely refers to that titled law, and the statutes-at-large has published the text of the law with that identifier.
+An example is ``Public Law 105-89, An Act: to promote the adoption of children in foster care.'' There is only one Public Law 105-89, it uniquely refers to that titled law, and the \emph{Statutes at Large} has published the text of the law with that identifier.
 \item Initially, laws were identified by a different system ("Early Regime").
-From the 1st through the 56th Congress, which concluded March 3, 1901, laws were identified in the Statutes at Large by chapter as well as Congress and session (e.g.
+From the 1st through the 56th Congress, which concluded March 3, 1901, laws were identified in the \emph{Statutes at Large} by chapter as well as Congress and session (e.g.
 ``Chapter 15, 56 Congress, Session 1, An Act: Relating to Cuban vessels.").
-All laws in the statutes-at-large are published with this information during the early period.
-The Early Regime and Later Regime are not interoperable, as the published pages of the statutes at large in the early period do not provide public law numbers and the published pages in later period do not provide chapters.
-\item For the 57th through 85th congress, the Statutes at Large uses both systems, but not always consistently.
+All laws in the \emph{Statutes at Large} are published with this information during the early period.
+The Early Regime and Later Regime are not interoperable, as the published pages of the \emph{Statutes at Large} in the early period do not provide public law numbers and the published pages in later period do not provide chapters.
+The early and later periods use fundamentally different citation systems.
+\item For the 57th through 85th congress, the \emph{Statutes at Large} uses both systems, but not always consistently, and not consistently in the same way as they would before or after.
 Indeed, a key difficulty in this period is that chapters and public laws are sometimes recycled within one Congress over multiple sessions of a particular Congress.\footnote{And worse, in just a few instances, the same session.
-Indeed, PL 65-246 refers to both a law ``Providing for the transportation from the District of Columbia of governmental employees whose services no longer are required." and also a law intended ``To authorize the sale of certain lands to school district numbered twenty-eight, of Missoula County, Montana."} Careful attention to chapters, public laws, and sessions does disambiguate nearly all laws, however these details are very particular and subtle.
+Indeed, PL 65-246 refers to both a law ``Providing for the transportation from the District of Columbia of governmental employees whose services no longer are required." and also a law intended ``To authorize the sale of certain lands to school district numbered twenty-eight, of Missoula County, Montana."} The law identification system that superficially seems to be inter-operable with both the prior and subsequent systems does not really work very well with either.
+Careful attention to chapters, public laws, and sessions does disambiguate nearly all laws, however these details are very particular and subtle.
+Caution is needed.
 \end{itemize}
 
- Following these citation practices, we used a rule-based parser to extract key pieces of information from scraped meta-data to build a database of laws.
+ Following these citation practices, we used a rule-based parser to extract key pieces of information from scraped meta-data and build a database of laws.
 Technical validation efforts revealed that there were occasional errors of transcription in our source data, for example mis-identification of chapters associated with laws or including page numbers that were not correct.
-Those errors that were found in the source data we corrected to conform with the text image captured on the HeinOnline site.
+Those errors that were found in the source data we corrected to conform with the text image captured on the HeinOnline site, although our guess is that there are others which have not been caught.
+Such issues highlight the needs for \textit{transparency} and \textit{reproducibility} in the process of data collection and data correction, as it is unlikely that any effort that lack either will avoid such issues.
 
@@
 The reference counts for total laws that we rely on comes from Appendix F reported in Galloway and Wise's History of the House of Representatives\nocite{gallowaywise}.
-It was the same set of reference counts previously used for validation and analysis by Ansolabhere, Palmer, and Schneer\cite{ansolabehere_palmer_schneer_2016}.
-Our definition of law is slightly more capacious than Galloway and Wise's, in the sense that we also consider "Joint Resolutions" laws, and the authors admit their own counts combine acts and resolutions (the latter of which are not, in our view, best understood as laws) from the 77th Congress and after.
+It was the same set of reference counts previously used for validation and analysis by Ansolabhere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016} Our definition of law is slightly more capacious than Galloway and Wise's, in the sense that we also consider "Joint Resolutions" laws, and the authors admit their own counts combine acts and resolutions (the latter of which are not, in our view, best understood as laws) from the 77th Congress and after.
 Nevertheless, it is possible to subset our data in such a way as to include the same set of documents as Galloway and Wise cover, and thereby constitute an appropriate test of technical validity.
@@
 
+The author would gratefully acknowledge the help of a number of research assistants, especially Jamie Gall, Kakshak Porwal, and Christina Leung, as well as funding through the Institute of Policy Research and Department of Political Science at Northwestern and the School of Global Strategy and Public Policy at University of California San Diego.
+
 \section*{Author contributions statement}
+
+B.L. was the sole contributor.
 

### 2023-09-27 draft/v1.tex
final submission changes
Updates from Overleaf

@@
 Also included in the repository are code and data used to validate the dataset as well as generate the figure.
-\footnote{\url{https://github.com/libgober/database_of_laws}}
+\footnote{\url{https://github.com/libgober/database_of_laws}}.
+Versions of these files used at time of submission to \textit{Scientific Data} are available in the OSF repository.
 
@@
 
+The author declares that he has no competing interests related to the research, authorship, or publication of this manuscript, and no conflicts of interest, financial or otherwise, exist.
 % The corresponding author is responsible for providing a \href{https://www.nature.com/sdata/policies/editorial-and-publishing-policies#competing}{competing interests statement} on behalf of all authors of the paper.

### 2023-11-08 draft/response.tex
added some response memo and so forth.

\documentclass{article}
\usepackage[margins=1in]{geometry}

\begin{document}
\flushleft
\noindent Manuscript Number: SDATA-23-01716 \newline
\noindent Manuscript Title: A Comprehensive Dataset of U.S. Federal Laws, 1789-2022  \newline

Dear Dr. Jones and Anonymous Reviewers,

I thank you for the opportunity to revise the manuscript in light of this important feedback. I will respond to each reviewer in turn.

\subsection*{Reviewer 1}

\begin{itemize}

\item More Information On How To Use This Data

I thank the reviewer for this suggestion. The usage section is now significantly enhanced. Whereas previously the section had only one paragraph it now has four paragraphs that describes in much greater detail how the dataset might be used. In particular, I emphasize that one can use the dataset to conduct comparisons between some focus set to laws and those that are outside the focus (i.e. number of laws enacted during divided government versus unified government over time), and also as skeleton for constructing a dataset of laws with multiple labels where one wishes to understand the relationship between the labels (i.e. ``laws enacted during unified government'' and ``relative importance of the law"). Given the diversity of possible projects that scholars might have, the goal was not to describe every use case, but to give a general feel for the merging tasks that most scholars would typically follow.  I have clarified as well the confusing line 185-6.

\item How To Find Full Text of the Law

I thank the reviewer for this suggestion. At some point, I had considered including these texts in the data release, however for reasons I now elaborate in the draft this was a significant undertaking in its own right and something that I have left for later. The problem is basically that the public full texts are very limited in coverage, so one needs to use proprietary sources for the most part. These sources such as ProQuest and HeinOnline have digitized and scanned a lot of laws, but acquiring copies of these electronic versions in a comprehensive way is difficult. There is some possibility of using one government source, but it needs to be investigated.

Given that a comprehensive database of law \textit{texts} would be another project, the question as I understand it is how to go about finding the text of any particular law. This is not very difficult given that the citation system I use mirrors closely the table of contents of the original source documents, the statutes at large. I have typically included page numbers where available, so volume and page of statute at large is easily searched on HeinOnline and ProQuest. Where not available, one can use the table of contents of these volumes.

\item Figure Improvement

\end{itemize}
\subsection*{Reviewer 2}

\end{document}

### 2023-11-08 draft/v1.tex
added some response memo and so forth.

@@
 Yet it is worth detailing the numerous and painstaking data collection efforts that have come increasingly close.
-Some of the earliest existing data responsive to these criteria comes from a key debate in American political science about the consequences of divided government.
+My focus is on public, scholarly data collection efforts that produce the kinds of tables that are appropriate for statistical analysis, rather than proprietary databases such as ProQuest Congressional or HeinOnline which are designed with such access constraints that researchers cannot easily use their contents for many important research purposes or validate what these datasets deliver.\footnote{This is not to say that such proprietary databases are not useful.
+Indeed, we rely on source material from HeinOnline extensively.
+That said, these proprietary sources do not provide the sort of database described in this report.} Some of the earliest existing data responsive to these criteria comes from a key debate in American political science about the consequences of divided government.
 In particular, scholars have wondered whether the state of unified government, where the President and Congress are controlled by the same party, is better or worse for legislative productivity than divided government, where these organs are not exclusively in controlled by the same political party.
@@
 
-The primary dataset we provide is publicly available at https://osf.io/qa289. Additionally, a Github repository that was used to construct the dataset will be made available upon publication.
+The primary dataset we provide is publicly available at \url{https://osf.io/qa289}.
+Additional data of interest used for validation is available within the files repository, available at \url{https://osf.io/mrghc}
 
@@
 
-While we provide a numeric identifier that can be used for referring to particular rows of our dataset, we recommend that future researchers use identification for laws that reflect greater attention to the inconsistencies in citation practice over time.
-In particular,  we recommend matching efforts that use piece-wise rules as outlined in the methods section above and implemented via special merging functions in the git repository.
+Our database presents a comprehensive table of U.S.
+laws.
+Depending on the research task, this table may receive different uses, and it is hard to anticipate all the places it will go.
+Having said that, we anticipate that scholars will frequently use this dataset by merging in some other dataset with labels, text, and so forth.
+Their research questions will presumably focus on the analysis of this meta-data about laws, possibly one at a time or perhaps in inter-relationship to one another.
+The research task about number of laws enacted during ``divided government" versus unified government is typical, for example, although perhaps too simple to see what the real challenge is because assigning the ``divided government" label requires the use of the ``date'' column.
+More challenging and typical would be adding labels that depend on individual identification of laws, for example the ``important" versus ``unimportant" distinction mentioned earlier.
+We presume that the scholar interested in our dataset has some set of laws $\mathcal{X}$ that they wish to merge to our data in order to compare laws that are in their set to laws that are outside their set.
+They would do so to illustrate what proportion of all laws their set of particular laws cover, for example, or to examine how some trends differ in their set versus outside their set differ.
+Often, scholars will have more than one set of laws that they are interested in, and their goal will be to setup a dataset involving sets of laws $\mathcal{X}$ and $\mathcal{Y}$.
+When working with multiple sets of partially overlapping lists of laws, it will often make sense to join both against a more comprehensive and universal set, as that keeps the scholars analytical options open.
+The basic question for using this data is what scholar needs to have in their source data to be able to use it.
+
+On the one hand, we provide a numeric identifier that scholars can include to unambiguously refer to a particular federal law.
+Moreover, we outline a procedure that should lead to consistent numeric identification even by other scholars on a going forward basis.
+While providing this identifier is generally a good idea to remove doubt about what law one is referring to, we understand that adoption of our identifiers by other scholars cannot be presumed.
+Additionally, if procedures were to change or their were additions, amendments, or deletions to future versions of our dataset, then there would be questions about backward compatibility.
+
+Therefore, in addition to referencing the identification system for laws we propose, we would also encourage scholars to pay attention to the citation systems as used in the source documents and record the necessary data accordingly.
+In particular, we recommend recording data and using matching based on the piece-wise rules as outlined in the methods section above and implemented via special merging functions in the git repository.
 Beginning with the 86th Congress laws should be matched using the public law number.
@@
 Generally, if public laws and chapters will be used to refer to laws in a dataset that is not exclusively relating to recent laws, one \textit{must} also include the Congressional session (or equivalently include the date of enactment, from which one can infer these details).
+While one often \textit{can} proceed to do matching without all these items, one runs a risk of problems, for example over-matching or mis-matching.
+More information such as bill title can certainly help to avoid ambiguities, but increasingly one will have a system of citation that is hard to make work across datasets.
+
+Finally, a brief word on enriching these data with full texts of U.S.
+laws.
+This dataset does not provide the texts of laws that are listed, although doing so would be an appropriate extension of this work.
+What this data set does provide is citation information on publicly available source documents, so typically linking the text once found is no more challenging than any other linking of label task described above.
+That said, getting clean texts of law is very difficult on a consistent basis from public sources.
+Post-1995 laws in electronic text format are available from the US government printing office.\footnote{\url{https://www.govinfo.gov/app/collection/plaw}} These laws are formatted using markup that allows one to place footnotes correctly and also separate various formatting materials, although at present writing it is not clear how consistently these formats have been used over the years.
+Since 2013, laws are also available in an XML markup format.
+Earlier laws in the \textit{Statutes at Large} that are still provided by the US GPO as PDFs, although for most text data projects one would need to then OCR the documents and this generates familiar issues.
+In terms of comprehensive sources of earlier laws, HeinOnline provides full texts of all laws in both PDF and OCRed text format.
+Proquest Congressional covers the Statutes at Large between 1789 and 2014, and also offers PDFs.\footnote{\url{https://proquest.libguides.com/congressionalhelp/ccc}} The only comprehensive public source for obtaining law texts of which we are aware is a viewing tool provided by the Office of Revision Counsel,\footnote{To find 14 Stat.
+41, for example, one can use this URL and it will generate an appropriate scan \url{https://uscode.house.gov/statviewer.htm?volume=14&page=41}} but the comprehensiveness of this data is untested at this point and the format is scanned PNGs rather than text or even PDF.
+Taking it as given that one can find the Statute at Large volume one wants, the citation information provided in the table is sufficient to conduct a table of contents search.
+Our data also does provide the page and volume number when readily available.
+Figure \ref{fig:toc} shows the table of contents of the statutes at large from both the "early" and "middle" citation regimes.
 
@@
 
-All code used to create the dataset from original sources, is available through a Github repository made public upon publication.
-Also included in the repository are code and data used to validate the dataset as well as generate the figure.
-\footnote{\url{https://github.com/libgober/database_of_laws}}.
-Versions of these files used at time of submission to \textit{Scientific Data} are available in the OSF repository.
+All code used to create the dataset from original sources, validate the dataset, as well as generate the figures are available at OSF repository.\footnote{\url{https://osf.io/mrghc} }
 

### 2023-11-08 draft/v1.tex
Finished tinkering with text of draft to deal with R1

@@
 federal laws, that is to say federal legislative enactments with a binding public character.
-Surprisingly, there is not, at least to the authors knowledge a transparent, fully comprehensive, and almost current database of these documents.
+Surprisingly, there is not, at least to the authors knowledge, a transparent, fully comprehensive, and almost current database of these documents.
 
@@
 Figure \ref{fig:totals} compares the counts for this key subset of our data.
-Note that in total Galloway and Wise count 23,155 laws, while we would peg the figure at 23,152, or three laws fewer ($\approx 0.13\%$ of the total).
+Note that in total Galloway and Wise count 23,155 laws between the 1st and 76th Congresses, while we would peg the figure at 23,152, or three laws fewer ($\approx 0.13\%$ of the total).
 The true discrepancy between our counts and Appendix F is somewhat greater, because in some years our counts are higher than Galloway \& Wise's and in some years lower.
@@
   \centering
-  \caption{Number of Acts of Congress by Meeting of Congress.}
+  \caption{Number of Acts of Congress by Meeting of Congress.
+Shading reflects total counts of all laws in our dataset, while the colored lines show the overlap in counts between our counts and the directly comparable subset of Galloway and Wise's counts.}
   \includegraphics[width=\linewidth]{draft/figures/counts_of_laws.png}

### 2023-11-08 analysis/scriptforggplot1.R
updated some figures

@@ -11,6 +11,9 @@ here::i_am("analysis/scriptforggplot1.R")
 #load data
 count_of_acts <- read_excel(here("build","count_of_acts.xlsx"))
 
+master_count = read_csv(here("build","master.csv")) %>%
+  group_by(congress_number) %>%
+  count()
 #rename
 count_of_acts <- count_of_acts %>%
   rename(galloway_count = "Galloway Counts")
@@ -30,6 +33,16 @@ pl <- ggplot(data = count_of_acts, aes(x = congress_number)) +
 print(pl)
 
 ggsave(pl,file = here("draft","figures","counts_of_laws.png"))
+
+pl_revised = pl +
+  geom_area(data=master_count,aes(y=n,x=congress_number),
+            alpha=0.2) + 
+  scale_x_continuous('Congress',breaks=c(1,20,40,60,76,100,117)) 
+
+ggsave(pl,file = here("draft","figures","counts_of_laws_revised.png"))
+
+
+
 #make difference column
 count_of_acts$difference <-  count_of_acts$galloway_count - count_of_acts$lib_count
 

### 2023-11-08 draft/response.tex
finished response memo

@@
 \documentclass{article}
-\usepackage[margins=1in]{geometry}
+\usepackage[margin=1in]{geometry}
 
@@
 
-\item Figure Improvement
+\item Showing Number of Laws in Full Data
+
+I thank the reviewer for the suggestion.
+After some experimentation, I decided that adding some shading instead of a line helped preserve the figures original legibility, but also accomplished the goal of showing that this full data covers a lot more years of legislative activity.
 
 \end{itemize}
+
 \subsection*{Reviewer 2}
 
+I thank the reviewer for the compliments toward the project and also for the question about ProQuest.
+I'll say a bit more bluntly here than I will in the draft: ProQuest likely does have this data or something very close to this on the backend powering their queries.
+Using ProQuest Congressional, it is possible to look up laws by page number and volume or volume and chapter.
+Doing at times returns multiple results, users are expected to click through and pick whichever one they are interested in, and then one can find details about the particular law such as Public Law number, date of passage, etc.
+\newline
+
+Given that, it's pretty clear that ProQuest is sitting on a database with a few tables that allow this querying to work.
+At the same time, these data are not in a readily accessible tabular format like this dataset or the kinds social scientists are accustomed to loading in R, STATA, etc.
+And you really need that tabular data to do a lot of different work (i.e.
+making figures like my Figure 1, or running a regression of legislative importance on divided government).
+There is no pathway that I can see to using ProQuest Congressional to get such a database, or if there is a path it would be an immense amount of RA work individually querying their systems (expensive) or scraping their proprietary data (dicey).
+Moreover, they have done no technical validation or described their process.
+Finally, their coverage stops in 2014, for whatever reason.
+\newline
+
+I make these same points a bit more subtly in the draft by talking about transparency, verification, and reliance on public sources, but I still hope that they convey the difference between what this data is and what ProQuest Congressional offers.
+ProQuest Congressional is good for more targeted searches and in depth research on particular laws, but it's not the right tool for broader analysis across many laws.
 \end{document}

### 2023-11-08 draft/v1.tex
finished response memo

@@
   \caption{Number of Acts of Congress by Meeting of Congress.
-Shading reflects total counts of all laws in our dataset, while the colored lines show the overlap in counts between our counts and the directly comparable subset of Galloway and Wise's counts.}
-  \includegraphics[width=\linewidth]{draft/figures/counts_of_laws.png}
+Shading reflects total counts of all laws in our dataset, while the colored lines show the overlap in directly comparable counts between subsets of Galloway and Wise and our data.}
+  \includegraphics[width=\linewidth]{draft/figures/counts_of_laws_revised.png}
     \label{fig:totals}

### 2023-11-16 draft/v1.tex
final edits for accepted stage

@@
 
-\title{A Comprehensive Dataset of U.S. Federal Laws, 1789-2022}
+\title{A comprehensive dataset of U.S. federal laws (1789-2022)}
 
@@
 \maketitle
-%  Click the title above to edit the author information and abstract
 
@@
 \section*{Background \& Summary}
-
-%(700 words maximum) An overview of the study design, the assay(s) performed, and the created data, including any background information needed to put this study in the context of previous work and the literature.
-The section should also briefly outline the broader goals that motivated the creation of this dataset and the potential reuse value.
-We also encourage authors to include a figure that provides a schematic overview of the study and assay(s) design.
-The Background \& Summary should not include subheadings.
-This section and the other main body sections of the manuscript should include citations to the literature as needed.
-
 What is a law?
@@
 And even then, there are exceptions and sub-divisions within these categories.
-``Private bills" granting relief in one-off cases\footnote{For example, last year Congress enacted a private law allowing Alaska-woman Rebecca Trimble to obtain permanent resident status, despite the fact the paperwork her adoptive parents had used to bring her to the United States from Mexico had been defective.} are typically not what scholars have in mind when one refers to ``laws.'' Nor are joint resolutions approving constitutional amendments which are not ratified by the states really laws (e.g.
+Last year Congress enacted a private law allowing Alaska-woman Rebecca Trimble to obtain permanent resident status, despite the fact the paperwork her adoptive parents had used to bring her to the United States from Mexico had been defective.
+Such ``private bills" granting relief in one-off cases are typically not what scholars have in mind when one refers to ``laws.'' Nor are joint resolutions approving constitutional amendments which are not ratified by the states really laws (e.g.
 the Equal Rights Amendment).
@@
 Yet it is worth detailing the numerous and painstaking data collection efforts that have come increasingly close.
-My focus is on public, scholarly data collection efforts that produce the kinds of tables that are appropriate for statistical analysis, rather than proprietary databases such as ProQuest Congressional or HeinOnline which are designed with such access constraints that researchers cannot easily use their contents for many important research purposes or validate what these datasets deliver.\footnote{This is not to say that such proprietary databases are not useful.
-Indeed, we rely on source material from HeinOnline extensively.
-That said, these proprietary sources do not provide the sort of database described in this report.} Some of the earliest existing data responsive to these criteria comes from a key debate in American political science about the consequences of divided government.
+My focus is on public, scholarly data collection efforts that produce the kinds of tables that are appropriate for statistical analysis, rather than proprietary databases such as ProQuest Congressional or HeinOnline which are designed with such access constraints that researchers cannot easily use their contents for many important research purposes or validate what these datasets deliver.
+Some of the earliest existing data responsive to these criteria comes from a key debate in American political science about the consequences of divided government.
 In particular, scholars have wondered whether the state of unified government, where the President and Congress are controlled by the same party, is better or worse for legislative productivity than divided government, where these organs are not exclusively in controlled by the same political party.
@@
 \cite{Howell2000} Clinton and Lapinski (2006) enter the same debate by introducing an IRT model for estimating the importance of enacted laws between 1877 and 1994,\cite{clinton2006measuring} and have subsequently used these same data and estimates to reconsider questions about the interpretation of roll-call votes as a measure of political ideology \cite{clinton2008laws,lapinski2008,bateman2017}.
-The Clinton-Lapinski model of legislative importance leverages an even more comprehensive assembly than the Howell et al effort, comprising some 37,766 law going all the way back to the post-Civil War era.\footnote{At present writing this database was avialable at one of the author's websites, \url{https://my.vanderbilt.edu/joshclinton/data/}} Yet to the authors knowledge, this comprehensive dataset has not been updated to include laws enacted in the last two decades.
+The Clinton-Lapinski model of legislative importance leverages an even more comprehensive assembly than the Howell et al effort, comprising some 37,766 law going all the way back to the post-Civil War era.
+Yet to the authors knowledge, this comprehensive dataset has not been updated to include laws enacted in the last two decades.
 Nor does it extend backwards into the first century of the U.S.
@@
 
-%There are several reasons why it is desirable to have a more complete dataset of U.S.
-lawmaking than has previously existed.
-Temporarlly In particular, minor legislation is usually major to somebody, otherwise why would someone go to the trouble of passing it?
-While focusing on the big pieces of legislation is perhaps appropriate for thinking about how party control effects the ability of collective government to solve the big problems, a more granular perspective is really necessary to think about how special interests may whittle away the gains made by broad coalitions through smaller pieces of legislation, or perhaps how policy fails to make the necessary incremental adjustments to keep with the times.
-There is notable inconsistency in what laws are included as significant using all these methods.
-The lack of a unified and complete dataset also frustrates progress of the discipline, as these authors do not necessarily use the same system to refer to particular laws, making U.S.
-law datasets used by social scientist far less inter-operable than they should be.
-The lack of inter-operability frustrates project
-
 This project seeks to build a comprehensive and easily updated list of U.S.
@@
 The most recent issue of the \emph{Statutes at Large} is from 2017, and it is published with about a six year delay.
-Even though the \emph{Statutes at Large} are not physically or electronically available for the last six years, the National Archives and Records Administration provides citations to page numbers almost immediately.\footnote{For example, on September 25, 2023 it was possible to get the statute at large citation of a law enacted only three days prior \url{https://web.archive.org/web/20230925173228/https://www.archives.gov/federal-register/laws/current.html}}
+Even though the \emph{Statutes at Large} are not physically or electronically available for the last six years, the National Archives and Records Administration provides citations to page numbers almost immediately.
+For example, on September 25, 2023 it was possible to get the statute at large citation of a law enacted only three days prior (\url{https://web.archive.org/web/20230925173228/https://www.archives.gov/federal-register/laws/current.html}).
 
@@
 Indeed, it is somewhat surprising that the U.S.
-government does not make electronic copies of the \emph{Statutes at Large} available prior to 1951,\footnote{https://www.govinfo.gov/app/collection/statute/2016} despite the fact that there were 64 earlier volumes containing laws that in many cases have not been amended.
+government does not make electronic copies of the \emph{Statutes at Large} available prior to 1951, despite the fact that there were 64 earlier volumes containing laws that in many cases have not been amended.
 In legal practice, not having these documents digitized usually works out well enough, because of ongoing public and private efforts to develop codices of laws, however there are occasional issues of interpretation where returning to the actual text of the law in the \emph{Statutes at Large} is necessary.
@@
 For older years that the GPO has not yet reached, we rely on the meta-data provided by HeinOnline.
-For more recent years where the \emph{Statutes at Large} do not yet exist, we rely on data on the National Archives website to supplement and bring our dataset to currency.\footnote{https://www.archives.gov/federal-register/laws.
+For more recent years where the \emph{Statutes at Large} do not yet exist, we rely on data on the National Archives website to supplement and bring our dataset to currency (\url{https://www.archives.gov/federal-register/laws}).
 Per that site, ``After the President signs a bill into law, it is delivered to the Office of the Federal Register (OFR)[, a division of the National Archives], where editors: assign a Public Law Number[,] prepare it for publication as a Slip Law[,] include it in the next edition of the United States \emph{Statutes at Large}.''}
@@
 \item For the 57th through 85th congress, the \emph{Statutes at Large} uses both systems, but not always consistently, and not consistently in the same way as they would before or after.
-Indeed, a key difficulty in this period is that chapters and public laws are sometimes recycled within one Congress over multiple sessions of a particular Congress.\footnote{And worse, in just a few instances, the same session.
-Indeed, PL 65-246 refers to both a law ``Providing for the transportation from the District of Columbia of governmental employees whose services no longer are required." and also a law intended ``To authorize the sale of certain lands to school district numbered twenty-eight, of Missoula County, Montana."} The law identification system that superficially seems to be inter-operable with both the prior and subsequent systems does not really work very well with either.
+Indeed, a key difficulty in this period is that chapters and public laws are sometimes recycled within one Congress over multiple sessions of a particular Congress.
+And worse, in just a few instances, the same session.
+Indeed, PL 65-246 refers to both a law ``Providing for the transportation from the District of Columbia of governmental employees whose services no longer are required." and also a law intended ``To authorize the sale of certain lands to school district numbered twenty-eight, of Missoula County, Montana." The law identification system that superficially seems to be inter-operable with both the prior and subsequent systems does not really work very well with either.
 Careful attention to chapters, public laws, and sessions does disambiguate nearly all laws, however these details are very particular and subtle.
@@
 
-% The Methods should include detailed text describing any steps or procedures used in producing the data, including full descriptions of the experimental design, data acquisition assays, and any computational processing (e.g.
-normalization, image feature extraction).
-See the detailed section in our submission guidelines for advice on writing a transparent and reproducible methods section.
-Related methods should be grouped under corresponding subheadings where possible, and methods should be described in enough detail to allow other researchers to interpret and repeat, if required, the full study.
-Specific data outputs should be explicitly referenced via data citation (see Data Records and Citing Data, below).
-
-% Authors should cite previous descriptions of the methods under use, but ideally the method descriptions should be complete enough for others to understand and reproduce the methods and processing steps without referring to associated publications.
-There is no limit to the length of the Methods section.
-Subheadings should not be numbered.
-
-% \subsection*{Subsection}
-
-% Example text under a subsection. Bulleted lists may be used where appropriate, e.g.
-
-% \begin{itemize}
-% \item First item
-% \item Second item
-% \end{itemize}
-
-% \subsubsection*{Third-level section}
-
-% Topical subheadings are allowed.
-
 \section*{Data Records}
 
-The primary dataset we provide is publicly available at \url{https://osf.io/qa289}.
+The primary dataset\cite{libgober_dataset} we provide is publicly available at \url{https://osf.io/qa289}.
 Additional data of interest used for validation is available within the files repository, available at \url{https://osf.io/mrghc}
-
-% The Data Records section should be used to explain each data record associated with this work, including the repository where this information is stored, and to provide an overview of the data files and their formats.
-Each external data record should be cited numerically in the text of this section, for example \cite{Hao:gidmaps:2014}, and included in the main reference list as described below.
-A data citation should also be placed in the subsection of the Methods containing the data-collection or analytical procedure(s) used to derive the corresponding record.
-Providing a direct link to the dataset may also be helpful to readers (\hyperlink{https://doi.org/10.6084/m9.figshare.853801}{https://doi.org/10.6084/m9.figshare.853801}).
-
-% Tables should be used to support the data records, and should clearly indicate the samples and subjects (study inputs), their provenance, and the experimental manipulations performed on each (please see 'Tables' below).
-They should also specify the data output resulting from each data-collection or analytical step, should these form part of the archived record.
 
@@
 
-% This section presents any experiments or analyses that are needed to support the technical quality of the dataset.
-This section may be supported by figures and tables, as needed.
-This is a required section; authors must present information justifying the reliability of their data.
-
-We offer two primary approaches to support the technical validation of our dataset.
-The first is to compare the total counts of laws by Congress against total counts previously published by social scientists.
+We offer two primary approaches to support the technical validation of our dataset.\cite{libgober_dataset} The first is to compare the total counts of laws by Congress against total counts previously published by social scientists.
 The second validation exercise involves showing that we cover well a particularly comprehensive dataset of laws published by the Office of Revision Counsel, the agency within Congress  responsible for preparing the U.S.
@@
 laws.
-The dataset we use is the table of official popular names for Congressional enactments as produced by the Office of Revision Counsel.\footnote{https://uscode.house.gov/popularnames/popularnames.htm} This table catalogues in its rows a set of 13,170 popular or short-names for official legal acts.
+The dataset we use is the table of official popular names for Congressional enactments as produced by the Office of Revision Counsel (\url{https://uscode.house.gov/popularnames/popularnames.htm}).
+This table catalogues in its rows a set of 13,170 popular or short-names for official legal acts.
 The table's rows have entries such as ``Obamacare," which directs readers to see another row on the ``Patient Protection and Affordable Care Act." In the row corresponding to the ``Patient Protection and Affordable Care Act," the table provide a citation ``Pub.
@@
 That said, getting clean texts of law is very difficult on a consistent basis from public sources.
-Post-1995 laws in electronic text format are available from the US government printing office.\footnote{\url{https://www.govinfo.gov/app/collection/plaw}} These laws are formatted using markup that allows one to place footnotes correctly and also separate various formatting materials, although at present writing it is not clear how consistently these formats have been used over the years.
+Post-1995 laws in electronic text format are available from the US Government Printing Office (\url{https://www.govinfo.gov/app/collection/plaw}).
+These laws are formatted using markup that allows one to place footnotes correctly and also separate various formatting materials, although at present writing it is not clear how consistently these formats have been used over the years.
 Since 2013, laws are also available in an XML markup format.
@@
 In terms of comprehensive sources of earlier laws, HeinOnline provides full texts of all laws in both PDF and OCRed text format.
-Proquest Congressional covers the Statutes at Large between 1789 and 2014, and also offers PDFs.\footnote{\url{https://proquest.libguides.com/congressionalhelp/ccc}} The only comprehensive public source for obtaining law texts of which we are aware is a viewing tool provided by the Office of Revision Counsel,\footnote{To find 14 Stat.
-41, for example, one can use this URL and it will generate an appropriate scan \url{https://uscode.house.gov/statviewer.htm?volume=14&page=41}} but the comprehensiveness of this data is untested at this point and the format is scanned PNGs rather than text or even PDF.
+Proquest Congressional covers the Statutes at Large between 1789 and 2014, and also offers PDFs (\url{https://proquest.libguides.com/congressionalhelp/ccc}).
+The only comprehensive public source for obtaining law texts of which we are aware is a viewing tool provided by the Office of Revision Counse.
+To find 14 Stat.
+41, for example, one can use this URL and it will generate an appropriate scan (\url{https://uscode.house.gov/statviewer.htm?volume=14&page=41}).
+Yet, the comprehensiveness of this data is untested at this point and the format is scanned PNGs rather than text or even PDF.
 Taking it as given that one can find the Statute at Large volume one wants, the citation information provided in the table is sufficient to conduct a table of contents search.
@@
 
-% The Usage Notes should contain brief instructions to assist other researchers with reuse of the data.
-This may include discussion of software packages that are suitable for analysing the assay data files, suggested downstream processing steps (e.g.
-normalization, etc.), or tips for integrating or comparing the data records with other datasets.
-Authors are encouraged to provide code, programs or data-processing workflows if they may help others understand or use the data.
-Please see our code availability policy for advice on supplying custom code alongside Data Descriptor manuscripts.
-
-% For studies involving privacy or safety controls on public access to the data, this section should describe in detail these controls, including how authors can apply to access the data, what criteria will be used to determine who may access the data, and any limitations on data use.
+\nocite{libgober_dataset}
 
@@
 
-All code used to create the dataset from original sources, validate the dataset, as well as generate the figures are available at OSF repository.\footnote{\url{https://osf.io/mrghc} }
-
-% For all studies using custom code in the generation or processing of datasets, a statement must be included under the heading "Code availability", indicating whether and how the code can be accessed, including any restrictions to access.
-This section should also include information on the versions of any software used, if relevant, and any specific variables or parameters used to generate, test, or process the current dataset.
+All code used to create the dataset from original sources, validate the dataset, as well as generate the figures are available at OSF repository (\url{https://osf.io/mrghc}).
 
@@
 
-% \noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu.
-Use the cite command for an inline citation, e.g.
-\cite{Kaufman2020, Figueredo:2009dg, Babichev2002, behringer2014manipulating}.
-For data citations of datasets uploaded to e.g.
-\emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.
-For journal articles, DOIs should be included for works in press that do not yet have volume or page numbers.
-For other journal articles, DOIs should be included uniformly for all articles or not at all.
-We recommend that you encode all DOIs in your bibtex database as full URLs, e.g.
-https://doi.org/10.1007/s12110-009-9068-2.
-
 \section*{Acknowledgements} (not compulsory)
-
-% Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
 
@@
 
-% Must include all authors, identified by initials, for example:
-% A.A. conceived the experiment(s), A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results. All authors reviewed the manuscript.
-
 \section*{Competing interests} (mandatory statement)
@@
 The author declares that he has no competing interests related to the research, authorship, or publication of this manuscript, and no conflicts of interest, financial or otherwise, exist.
-% The corresponding author is responsible for providing a \href{https://www.nature.com/sdata/policies/editorial-and-publishing-policies#competing}{competing interests statement} on behalf of all authors of the paper.
-This statement must be included in the submitted article file.
 
@@
 
-% Figures, tables, and their legends, should be included at the end of the document.
-Figures and tables can be referenced in \LaTeX{} using the ref command, e.g.
-Figure \ref{fig:stream} and Table \ref{tab:example}.
-
-% Authors are encouraged to provide one or more tables that provide basic information on the main ‘inputs’ to the study (e.g.
-samples, participants, or information sources) and the main data outputs of the study.
-Tables in the manuscript should generally not be used to present primary data (i.e.
-measurements).
-Tables containing primary data should be submitted to an appropriate data repository.
-
-% Tables may be provided within the \LaTeX{} document or as separate files (tab-delimited text or Excel files).
-Legends, where needed, should be included here.
-Generally, a Data Descriptor should have fewer than ten Tables, but more may be allowed when needed.
-Tables may be of any size, but only Tables which fit onto a single printed page will be included in the PDF version of the article (up to a maximum of three).
-
-% Due to typesetting constraints, tables that do not fit onto a single A4 page cannot be included in the PDF version of the article and will be made available in the online version only.
-Any such tables must be labelled in the text as ‘Online-only’ tables and numbered separately from the main table list e.g.
-‘Table 1, Table 2, Online-only Table 1’ etc.
-
-% \begin{figure}[ht]
-% \centering
-% \includegraphics[width=\linewidth]{./assets/stream}
-% \caption{Legend (350 words max). Example legend text.}
-% \label{fig:stream}
-% \end{figure}
-
-% \begin{table}[ht]
-% \centering
-% \begin{tabular}{|l|l|l|}
-% \hline
-% Condition & n & p \\
-% \hline
-% A & 5 & 0.1 \\
-% \hline
-% B & 10 & 0.01 \\
-% \hline
-% \end{tabular}
-% \caption{\label{tab:example}Legend (350 words max). Example legend text.}
-% \end{table}
-
 \end{document}
